---
title: "Atlantic Shores"
format: html
editor: visual
css: styles.css
editor_options: 
  chunk_output_type: console
---

## Project 212520, 218270 (*Fugro Enterprise)* and Project 217344, 221851 *(Bella Maria*)

### Operation Activity

Total hours of sparker operation:

```{r}
#| echo: false
#| warning: false

setwd('C:/Users/nicole.mucci/Documents/R/PEMAD-MDEB-PSO')
#load libraries
library(readr)
library(tidyverse)
library(dplyr)
library(tidyr)
library(stringr)
library(gt)

#import tidy data
visualdetect <- readr::read_csv("data/AtlanticShores/AtlanticShores_VisualDetect_Tidy.csv", locale = locale(encoding = "latin1"))
effort <- readr::read_csv("data/AtlanticShores/AtlanticShores_Effort_Tidy.csv", locale = locale(encoding = "latin1"))
operations <- readr::read_csv("data/AtlanticShores/AtlanticShores_Operations_Tidy.csv", locale = locale(encoding = "latin1"))
#portcall <- readr::read_csv("data/COSW/COSW_PortCall_Tidy.csv", locale = locale(encoding = "latin1"))
project <- readr::read_csv("data/AtlanticShores/AtlanticShores_Project.csv", locale = locale(encoding = "latin1"))
#Fugro Enterprise
operations_fugro <- operations %>% filter(VESSEL == "Fugro Enterprise") 

sparker_sursource <- operations_fugro %>% hms(operations_fugro$DUR_SURSOURCE) %>% period_to_seconds()
sparker_sursource <- (((sum(sparker_sursource, na.rm=TRUE))/60)/60)

sparker_soft <- operations_fugro %>% hms(operations_fugro$DUR_SOFTSTART) %>% period_to_seconds()
sparker_soft <- (((sum(sparker_soft, na.rm=TRUE))/60)/60)

sparker_test <- operations_fugro %>% hms(operations_fugro$DUR_TEST) %>% period_to_seconds()
sparker_test <- (((sum(sparker_test, na.rm=TRUE))/60)/60)

sparker_presursource <- operations_fugro %>% hms(operations_fugro$DUR_PRESURSOURCE) %>% period_to_seconds()
sparker_presursource <- (((sum(sparker_presursource, na.rm=TRUE))/60)/60)

sparker_postsur <- operations_fugro %>% hms(operations_fugro$DUR_POSTSUR) %>% period_to_seconds()
sparker_postsur <- (((sum(sparker_postsur, na.rm=TRUE))/60)/60)

total_sparkerop_fugro <- sum(sparker_sursource, sparker_soft, sparker_test, sparker_presursource, sparker_postsur)
#Bella Maria
operations_bella <- operations %>% filter(VESSEL == "Bella Maria") 

sparker_sursource <- operations_bella %>% hms(operations_bella$DUR_SURSOURCE) %>% period_to_seconds()
sparker_sursource <- (((sum(sparker_sursource, na.rm=TRUE))/60)/60)

sparker_soft <- operations_bella %>% hms(operations_bella$DUR_SOFTSTART) %>% period_to_seconds()
sparker_soft <- (((sum(sparker_soft, na.rm=TRUE))/60)/60)

sparker_test <- operations_bella %>% hms(operations_bella$DUR_TEST) %>% period_to_seconds()
sparker_test <- (((sum(sparker_test, na.rm=TRUE))/60)/60)

sparker_presursource <- operations_bella %>% hms(operations_bella$DUR_PRESURSOURCE) %>% period_to_seconds()
sparker_presursource <- (((sum(sparker_presursource, na.rm=TRUE))/60)/60)

sparker_postsur <- operations_bella %>% hms(operations_bella$DUR_POSTSUR) %>% period_to_seconds()
sparker_postsur <- (((sum(sparker_postsur, na.rm=TRUE))/60)/60)

total_sparkerop_bella <- sum(sparker_sursource, sparker_soft, sparker_test, sparker_presursource, sparker_postsur)

vessel <- c("Fugro Enterprise", "Bella Maria")
date <- c("4/20/2022 - 9/13/2022; 8/9/2023 - 8/23/2023", "4/21/2022 - 6/24/2022; 7/20/2023 - 8/28/2023")
operation <- c(total_sparkerop_fugro, total_sparkerop_bella)%>% round(digits=2)
df <- data.frame(vessel = vessel, date=date, operation = operation)

op_table <- gt(df) %>% cols_label(vessel = "Survey Vessel", date= "Dates of Operation", operation= "Total Hours of Source Operation (HH.HH)")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
op_table
```

### Monitoring Effort

Summary of monitoring effort:

```{r}
#| echo: false
#| warning: false

day_obs <- hms(effort$VIS_DAY_OBS)
night_obs <- hms(effort$VIS_NIGHT_OBS)
#no acoustic observations
day_obs_sec <- period_to_seconds(day_obs)
day_obs_hrs <- (((sum(day_obs_sec, na.rm=TRUE))/60)/60)
night_obs_sec <- period_to_seconds(night_obs)
night_obs_hrs <- (((sum(night_obs_sec, na.rm=TRUE))/60)/60)
total_obs <- (day_obs_hrs + night_obs_hrs)
#sparkers active 

sparkers_day <- (hms(effort$SOURCE_DAY_OBS))
sparkers_day_sec <- period_to_seconds(sparkers_day)
sparkers_day_hrs <- (((sum(sparkers_day_sec, na.rm=TRUE))/60)/60)
silent_day <- day_obs_hrs - sparkers_day_hrs 

sparkers_nite <- hms(effort$SOURCE_NIGHT_OBS)
sparkers_nite_sec <- period_to_seconds(sparkers_nite)
sparkers_nite_hrs <- (((sum(sparkers_nite_sec, na.rm=TRUE))/60)/60)
silent_night <- night_obs_hrs - sparkers_nite_hrs

sparkers_pam <- hms(effort$SOURCE_VIS_PAM_NIGHT)
sparkers_pam_sec <- period_to_seconds(sparkers_pam)
sparkers_pam_hrs <- (((sum(sparkers_pam_sec, na.rm=TRUE))/60)/60)
pam_night<- hms(effort$VIS_PAM_NIGHT_OBS)
pam_night_sec <- period_to_seconds(pam_night)
pam_night_hrs <- (((sum(pam_night_sec , na.rm=TRUE))/60)/60)
silent_pam <- pam_night_hrs - sparkers_pam_hrs

monitoring <- c("Source active-daytime", "Source silent-daytime", "Source active-nighttime", "Source silent-nighttime", "Souce active-PAM", "Source silent-PAM", "Total")
visual <- c(sparkers_day_hrs, silent_day, sparkers_nite_hrs, silent_night,sparkers_pam_hrs,silent_pam,total_obs) %>% round(digits=2)


df <- data.frame(Monitoring=monitoring, Visual = visual)

monitoring_table <- gt(df) %>% cols_label(Monitoring = "Monitoring Effort by Source Activity", Visual= "Visual (HH.HH)")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
monitoring_table
```

### Environmental Conditions

Summary of visibility conditions during the survey:

```{r}
#| echo: false
#| warning: false

#print(unique(effort$VISIBIL))

#visibility conditions
#monitoring effort with >5 km visibiilIty 
effort_highvis <- filter(effort, VISIBIL == ">5")
effort_high <- hms(effort_highvis$VIS_DAY_OBS) %>% period_to_seconds()
effort_high <- (((sum(effort_high, na.rm=TRUE))/60)/60)
effort_high_PV <- hms(effort_highvis$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_high_PV <- (((sum(effort_high_PV, na.rm=TRUE))/60)/60)
effort_night <- hms(effort_highvis$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_night <- (((sum(effort_night, na.rm=TRUE))/60)/60)
effort_high_P <- hms(effort_highvis$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_high_P <- (((sum(effort_high_P, na.rm=TRUE))/60)/60)
greater_five <- (effort_high + effort_high_PV + effort_night + effort_high_P)

effort_midvis <- filter(effort, VISIBIL == "2-5")
effort_midvis_day <- hms(effort_midvis$VIS_DAY_OBS) %>% period_to_seconds()
effort_midvis_day <- (((sum(effort_midvis_day, na.rm=TRUE))/60)/60)
effort_midvis_night <- hms(effort_midvis$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_midvis_night <- (((sum(effort_midvis_night, na.rm=TRUE))/60)/60)
effort_midvis_PV <- hms(effort_midvis$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_midvis_PV <- (((sum(effort_midvis_PV, na.rm=TRUE))/60)/60)
effort_midvis_P <- hms(effort_midvis$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_midvis_P <- (((sum(effort_midvis_P, na.rm=TRUE))/60)/60)

two_to_five <- (effort_midvis_day + effort_midvis_night + effort_midvis_P + effort_midvis_PV)

effort_lowvis <- filter(effort, VISIBIL == "0.5-1" | VISIBIL == "1-2" | VISIBIL == "0.05-0.1" |VISIBIL == "0.3-0.5" | VISIBIL == "<.05" |VISIBIL == "0.1-0.3" )
effort_lowvis_day <- hms(effort_lowvis$VIS_DAY_OBS) %>% period_to_seconds()
effort_lowvis_day <- (((sum(effort_lowvis_day, na.rm=TRUE))/60)/60)
effort_lowvis_night <- hms(effort_lowvis$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_lowvis_night <- (((sum(effort_lowvis_night, na.rm=TRUE))/60)/60)
effort_lowvis_PV <- hms(effort_lowvis$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_lowvis_PV <- (((sum(effort_lowvis_PV, na.rm=TRUE))/60)/60)
effort_lowvis_P <- hms(effort_lowvis$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_lowvis_P <- (((sum(effort_lowvis_P, na.rm=TRUE))/60)/60)

less_than_2 <- (effort_lowvis_P + effort_lowvis_PV + effort_lowvis_night + effort_lowvis_day)

Visibility <- c("Greater than 5 km", "2 to 5 km", "Less than 2 km")
Duration <- c(greater_five, two_to_five, less_than_2) %>% round(digits=2)
df<- data.frame(Visibility=Visibility, Duration=Duration)
  
visibility_table <- gt(df) %>% cols_label(Visibility = "Visibility", Duration= "Duration (HH.HH)")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
visibility_table
```

Beaufort Sea State during the survey:

```{r}
#| echo: false
#| warning: false

#Beaufort Sea State during monitoring
#B0
effort_B0 <- filter(effort, BEAUF == 0)
effort_B0_day <- hms(effort_B0$VIS_DAY_OBS) %>% period_to_seconds()
effort_B0_day <- (((sum(effort_B0_day, na.rm=TRUE))/60)/60)
effort_B0_night <- hms(effort_B0$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B0_night <- (((sum(effort_B0_night, na.rm=TRUE))/60)/60)
effort_B0_PAM <- hms(effort_B0$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B0_PAM <- (((sum(effort_B0_PAM, na.rm=TRUE))/60)/60)
effort_B0_P <- hms(effort_B0$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_B0_P <- (((sum(effort_B0_P, na.rm=TRUE))/60)/60)
b0 <- (effort_B0_day + effort_B0_night + effort_B0_PAM + effort_B0_P)
#B1 
effort_B1 <- filter(effort, BEAUF == 1)
effort_B1_day <- hms(effort_B1$VIS_DAY_OBS) %>% period_to_seconds()
effort_B1_day <- (((sum(effort_B1_day, na.rm=TRUE))/60)/60)
effort_B1_night <- hms(effort_B1$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B1_night <- (((sum(effort_B1_night, na.rm=TRUE))/60)/60)
effort_B1_PAM <- hms(effort_B1$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B1_PAM <- (((sum(effort_B1_PAM, na.rm=TRUE))/60)/60)
effort_B1_P <- hms(effort_B1$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_B1_P <- (((sum(effort_B1_P, na.rm=TRUE))/60)/60)
b1 <- (effort_B1_day + effort_B1_night + effort_B1_PAM + effort_B1_P)
#B2
effort_B2 <- filter(effort, BEAUF == 2)
effort_B2_day <- hms(effort_B2$VIS_DAY_OBS) %>% period_to_seconds()
effort_B2_day <- (((sum(effort_B2_day, na.rm=TRUE))/60)/60)
effort_B2_night <- hms(effort_B2$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B2_night <- (((sum(effort_B2_night, na.rm=TRUE))/60)/60)
effort_B2_PAM <- hms(effort_B2$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B2_PAM <- (((sum(effort_B2_PAM, na.rm=TRUE))/60)/60)
effort_B2_P <- hms(effort_B2$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_B2_P <- (((sum(effort_B2_P, na.rm=TRUE))/60)/60)
b2 <- (effort_B2_day + effort_B2_night + effort_B2_PAM +effort_B2_P)
#B3
effort_B3 <- filter(effort, BEAUF == 3)
effort_B3_day <- hms(effort_B3$VIS_DAY_OBS) %>% period_to_seconds()
effort_B3_day <- (((sum(effort_B3_day, na.rm=TRUE))/60)/60)
effort_B3_night <- hms(effort_B3$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B3_night <- (((sum(effort_B3_night, na.rm=TRUE))/60)/60)
effort_B3_PAM <- hms(effort_B3$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B3_PAM <- (((sum(effort_B3_PAM, na.rm=TRUE))/60)/60)
effort_B3_PAM_d <- hms(effort_B3$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_B3_PAM_d <- (((sum(effort_B3_PAM_d, na.rm=TRUE))/60)/60)
b3<-(effort_B3_day + effort_B3_night + effort_B3_PAM+effort_B3_PAM_d)
#B4
effort_B4 <- filter(effort, BEAUF == 4)
effort_B4_day <- hms(effort_B4$VIS_DAY_OBS) %>% period_to_seconds()
effort_B4_day <- (((sum(effort_B4_day, na.rm=TRUE))/60)/60)
effort_B4_night <- hms(effort_B4$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B4_night <- (((sum(effort_B4_night, na.rm=TRUE))/60)/60)
effort_B4_PAM <- hms(effort_B4$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B4_PAM <- (((sum(effort_B4_PAM, na.rm=TRUE))/60)/60)
b4<-(effort_B4_day + effort_B4_night + effort_B4_PAM)
#B5
effort_B5 <- filter(effort, BEAUF == 5)
effort_B5_day <- hms(effort_B5$VIS_DAY_OBS) %>% period_to_seconds()
effort_B5_day <- (((sum(effort_B5_day, na.rm=TRUE))/60)/60)
effort_B5_night <- hms(effort_B5$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B5_night <- (((sum(effort_B5_night, na.rm=TRUE))/60)/60)
effort_B5_PAM <- hms(effort_B5$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B5_PAM <- (((sum(effort_B5_PAM, na.rm=TRUE))/60)/60)
b5<-(effort_B5_day + effort_B5_night + effort_B5_PAM)
#B6
effort_B6 <- filter(effort, BEAUF == 6)
effort_B6_day <- hms(effort_B6$VIS_DAY_OBS) %>% period_to_seconds()
effort_B6_day <- (((sum(effort_B6_day, na.rm=TRUE))/60)/60)
effort_B6_night <- hms(effort_B6$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B6_night <- (((sum(effort_B6_night, na.rm=TRUE))/60)/60)
effort_B6_PAM <- hms(effort_B6$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B6_PAM <- (((sum(effort_B6_PAM, na.rm=TRUE))/60)/60)
b6<-(effort_B6_day + effort_B6_night + effort_B6_PAM)
#B7
effort_B7 <- filter(effort, BEAUF == 7)
effort_B7_day <- hms(effort_B7$VIS_DAY_OBS) %>% period_to_seconds()
effort_B7_day <- (((sum(effort_B7_day, na.rm=TRUE))/60)/60)
effort_B7_night <- hms(effort_B7$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B7_night <- (((sum(effort_B7_night, na.rm=TRUE))/60)/60)
effort_B7_PAM <- hms(effort_B7$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B7_PAM <- (((sum(effort_B7_PAM, na.rm=TRUE))/60)/60)
b7<-(effort_B7_day + effort_B7_night + effort_B7_PAM)
#B8
effort_B8 <- filter(effort, BEAUF == 8)
effort_B8_day <- hms(effort_B8$VIS_DAY_OBS) %>% period_to_seconds()
effort_B8_day <- (((sum(effort_B8_day, na.rm=TRUE))/60)/60)
effort_B8_night <- hms(effort_B8$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B8_night <- (((sum(effort_B8_night, na.rm=TRUE))/60)/60)
effort_B8_PAM <- hms(effort_B8$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B8_PAM <- (((sum(effort_B8_PAM, na.rm=TRUE))/60)/60)
b8<-(effort_B8_day + effort_B8_night + effort_B8_PAM)
#B9
effort_B9 <- filter(effort, BEAUF == 9)
effort_B9_day <- hms(effort_B9$VIS_DAY_OBS) %>% period_to_seconds()
effort_B9_day <- (((sum(effort_B9_day, na.rm=TRUE))/60)/60)
effort_B9_night <- hms(effort_B9$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B9_night <- (((sum(effort_B9_night, na.rm=TRUE))/60)/60)
effort_B9_PAM <- hms(effort_B9$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B9_PAM <- (((sum(effort_B9_PAM, na.rm=TRUE))/60)/60)
b9<-(effort_B9_day + effort_B9_night + effort_B9_PAM)

total <- b0+b1+ b2+b3+b4+b5+b6+b7+b8+b9
Beaufort = c("B0", "B1", "B2", "B3", "B4","B5","B6","B7","B8","B9", "Total")
Duration <- c(b0, b1, b2, b3, b4,b5,b6,b7,b8,b9, total)%>% round(digits=2)
df<- data.frame(Beaufort=Beaufort, Duration=Duration)
  
Beauf_table <- gt(df) %>% cols_label(Beaufort = "Beaufort Sea State", Duration= "Duration (HH.HH)")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
Beauf_table
```

Swell height during monitoring during the survey:

```{r}
#| echo: false
#| warning: false

#print(unique(effort$SWELL))

lowswell <- filter(effort, SWELL == "<2")
s_day <- hms(lowswell$VIS_DAY_OBS) %>% period_to_seconds()
s_day <- (((sum(s_day, na.rm=TRUE))/60)/60)
s_night <- hms(lowswell$VIS_NIGHT_OBS) %>% period_to_seconds()
s_night <- (((sum(s_night, na.rm=TRUE))/60)/60)
s_PAM <- hms(lowswell$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
s_PAM <- (((sum(s_PAM, na.rm=TRUE))/60)/60)
d_PAM <- hms(lowswell$VIS_PAM_DAY_OBS) %>% period_to_seconds()
d_PAM <- (((sum(d_PAM, na.rm=TRUE))/60)/60)
low_swell <- (s_day + s_night + s_PAM + d_PAM)

midswell <- filter(effort, SWELL == "2-4")
m_day <- hms(midswell$VIS_DAY_OBS) %>% period_to_seconds()
m_day <- (((sum(m_day, na.rm=TRUE))/60)/60)
m_night <- hms(midswell$VIS_NIGHT_OBS) %>% period_to_seconds()
m_night <- (((sum(m_night, na.rm=TRUE))/60)/60)
m_PAM <- hms(midswell$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
m_PAM <- (((sum(m_PAM, na.rm=TRUE))/60)/60)
mid_swell <- (m_day + m_night + m_PAM)

Swell = c("Less than 2 m", "2 to 4 m")
Duration <- c(low_swell, mid_swell)%>% round(digits=2)
df<- data.frame(Swell=Swell, Duration=Duration)
  
Swell_table <- gt(df) %>% cols_label(Swell = "Swell", Duration= "Duration (HH.HH)")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
Swell_table
```

### Visual Detections

Total number of detection events by species:

```{r}
#| echo: false
#| warning: false

#detections by species
species_summary <- visualdetect %>%
  count(NAME_COMMON)
species_table <- gt(species_summary) %>% cols_label(NAME_COMMON = "Species",
                                          n = "Number of detection records")%>% tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
species_table
```

Total detected individuals by species, and detection and distance summaries:

```{r}
#| echo: false
#| warning: false
#visualdetect_westerly$RANGE_VESSEL_START <- as.numeric(visualdetect_westerly$RANGE_VESSEL_START)

individuals_summary <- visualdetect %>%
  group_by(NAME_COMMON) %>%
  summarize(
    total_value = sum(TOT_NUM),
            average_value = round(mean(TOT_NUM),1),
            dist_value = round(mean(RANGE_VESSEL_START),0))

ind_table <- gt(individuals_summary) %>% cols_label(NAME_COMMON = "Species",
                  total_value = "Individuals Count",
                  average_value = "Average group size",
                  dist_value = "Average distance (m) at first detection")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )

ind_table
```

Closest point of approach (CPA) to source (sparker) during detections:

\[MEAN CPA TO SILENT SOURCE FOR UNIDENTIFIED DOLPHIN, HUMPBACK WHALE, UNIDENTIFIED WHALE ; MEAN CPA TO ACTIVE SOURCE FOR HUMPBACK WHALE DIFFERENT THAN WHAT WAS REPORTED\]

```{r}
#| echo: false
#| warning: false

CPA <- visualdetect%>%
  group_by(NAME_COMMON) %>%
  summarize(active_value = round(mean(MITZONE_ACTIVESOURCE_DIST, na.rm = TRUE),2),
            inactive_value = round(mean(MITZONE_SILENTSOURCE_DIST, na.rm = TRUE),2))

CPA_table <- gt(CPA) %>% cols_label(NAME_COMMON = "Species",
                  active_value = "Mean CPA to active sparker (meters)",
                  inactive_value = "Mean CPA to silent sparker (meters)") %>%  tab_options(
    data_row.padding = px(1),
    table.align = "left")

CPA_table
```

### Incidental Harassment Authorization (IHA) Level B Exposures

```{r}
#| echo: false
#| warning: false

take <- visualdetect %>% group_by(NAME_COMMON) %>%   
  summarize(take_value = sum(LEVELB_TAKE, na.rm = TRUE))   

take_table <- gt(take) %>% cols_label(NAME_COMMON = "Species", take_value = "Total Number of Animals Observed Inside the Level B Harassment Zone") %>%  tab_options(     data_row.padding = px(1),     table.align = "left"   )  

take_table
```
