---
title: "Attentive Energy"
format: html
editor: visual
css: styles.css
editor_options: 
  chunk_output_type: console
---

------------------------------------------------------------------------

## Project 222076 (*Marcelle Bordelon*)

### Operation Activity

Total hours of sparker operation:

```{r}
#| echo: false
#| warning: false

setwd('C:/Users/nicole.mucci/Documents/R/PEMAD-MDEB-PSO')
#load libraries
library(readr)
library(tidyverse)
library(dplyr)
library(tidyr)
library(stringr)
library(gt)

operations <- readr::read_csv("data/Attentive/Attentive2023_Operations_Tidy.csv")
visualdetect<- readr::read_csv("data/Attentive/Attentive2023_VisualDetect_Tidy.csv")
effort <- readr::read_csv("data/Attentive/Attentive2023_Effort_Tidy.csv")
operations <- readr::read_csv("data/Attentive/Attentive2023_Operations_Tidy.csv")
portcall <- readr::read_csv("data/Attentive/Attentive2023_PortCall_Tidy.csv")
acousticdetect <- readr::read_csv("data/Attentive/Attentive2023_AcousticDetect_Tidy.csv")
portcall <- readr::read_csv("data/Attentive/Attentive2023_PortCall_Tidy.csv", locale = locale(encoding = "latin1"))

operations_marcelle <- operations %>% filter(VESSEL == "Marcelle Bordelon") %>% filter(PROJECT_NUMBER == 222076)

sparker_sursource <- operations_marcelle %>% hms(operations_marcelle$DUR_SURSOURCE) %>% period_to_seconds()
sparker_sursource <- (((sum(sparker_sursource, na.rm=TRUE))/60)/60)

sparker_soft <- operations_marcelle %>% hms(operations_marcelle$DUR_SOFTSTART) %>% period_to_seconds()
sparker_soft <- (((sum(sparker_soft, na.rm=TRUE))/60)/60)

sparker_test <- operations_marcelle %>% hms(operations_marcelle$DUR_TEST) %>% period_to_seconds()
sparker_test <- (((sum(sparker_test, na.rm=TRUE))/60)/60)

sparker_presursource <- operations_marcelle %>% hms(operations_marcelle$DUR_PRESURSOURCE) %>% period_to_seconds()
sparker_presursource <- (((sum(sparker_presursource, na.rm=TRUE))/60)/60)

sparker_postsur <- operations_marcelle %>% hms(operations_marcelle$DUR_POSTSUR) %>% period_to_seconds()
sparker_postsur <- (((sum(sparker_postsur, na.rm=TRUE))/60)/60)

total_sparkerop <- sum(sparker_sursource, sparker_soft, sparker_test, sparker_presursource, sparker_postsur)

vessel <- c("Marcelle Bordelon")
date <- c("9/3/2023 - 12/25/2023")
operation <- c(total_sparkerop)%>% round(digits=2)
df <- data.frame(vessel = vessel, date=date, operation = operation)

op_table <- gt(df) %>% cols_label(vessel = "Survey Vessel", date= "Dates of Operation", operation= "Total Hours of Source Operation (HH.HH)")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
op_table
```

### Monitoring Effort

```{r}
#| echo: false
#| warning: false

effort_mar <- effort %>% filter(VESSEL == "Marcelle Bordelon") %>% filter(PROJECT_NUMBER == 222076)
day_obs <- hms(effort_mar$VIS_DAY_OBS)
night_obs <- hms(effort_mar$VIS_NIGHT_OBS)
acous_obs <- hms(effort_mar$VIS_PAM_NIGHT_OBS)
day_obs_sec <- period_to_seconds(day_obs)
day_obs_hrs <- (((sum(day_obs_sec, na.rm=TRUE))/60)/60)
#sparkers active 
sparkers_day <- hms(effort_mar$SOURCE_DAY_OBS)
sparkers_day_sec <- period_to_seconds(sparkers_day)
sparkers_day_hrs <- (((sum(sparkers_day_sec, na.rm=TRUE))/60)/60)
sparkers_nite <- hms(effort_mar$SOURCE_NIGHT_OBS)
sparkers_nite_sec <- period_to_seconds(sparkers_nite)
sparkers_nite_hrs <- (((sum(sparkers_nite_sec, na.rm=TRUE))/60)/60)
sparkers_day_pam <- hms(effort_mar$SOURCE_VIS_PAM_DAY)
sparkers_day_pam_sec <- period_to_seconds(sparkers_day_pam)
sparkers_day_pam_hrs <- (((sum(sparkers_day_pam_sec, na.rm=TRUE))/60)/60)
sparkers_nite_pam <- hms(effort_mar$SOURCE_VIS_PAM_NIGHT)
sparkers_nite_pam_sec <- period_to_seconds(sparkers_nite_pam)
sparkers_nite_pam_hrs <- (((sum(sparkers_nite_pam_sec, na.rm=TRUE))/60)/60)
sparkers_active <- sum(sparkers_nite_hrs + sparkers_day_hrs + sparkers_nite_pam_hrs+ sparkers_day_pam_hrs)

#PAM daytime and nighttime
pam_day<- hms(effort_mar$VIS_PAM_DAY_OBS)
pam_day_sec <- period_to_seconds(pam_day)
pam_day_hrs <- (((sum(pam_day_sec, na.rm=TRUE))/60)/60)
pam_night<- hms(effort_mar$VIS_PAM_NIGHT_OBS)
pam_night_sec <- period_to_seconds(pam_night)
pam_night_hrs <- (((sum(pam_night_sec , na.rm=TRUE))/60)/60)

night_obs_sec <- period_to_seconds(night_obs)
night_obs_hrs <- (((sum(night_obs_sec, na.rm=TRUE))/60)/60)

acous_obs_sec <- period_to_seconds(acous_obs)
acous_obs_hrs <- (((sum(acous_obs_sec, na.rm=TRUE))/60)/60)

total_day <- day_obs_hrs + pam_day_hrs
total_night <- night_obs_hrs + pam_night_hrs
total_vis <- total_day + total_night
total_pam <- pam_day_hrs + pam_night_hrs
total_obs <- (day_obs_hrs + night_obs_hrs + total_pam)
```

Summary of monitoring effort:

```{r}
#| echo: false
#| warning: false

monitoring <- c("Sparker active", "Sparker not active", "Daytime", "Nighttime", "Total")
visual <- c(sparkers_active, (total_vis - sparkers_active), total_day,  total_night, total_obs) %>% round(digits=2)
PAM <- c(sparkers_nite_pam_hrs, (total_pam - sparkers_nite_pam_hrs),pam_day_hrs,  pam_night_hrs, total_pam)%>% round(digits=2)

df <- data.frame(Monitoring=monitoring, Visual = visual, PAM= PAM)

monitoring_table <- gt(df) %>% cols_label(Monitoring = "Monitoring effort", Visual= "Visual (HH.HH)", PAM= "PAM (HH.HH)")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
monitoring_table
```

Note that there are missing links in the original dataset in the "SOURCE_DAY_OBS" column. Therefore, the calculated monitoring effort hours for when the sparkers are active and inactive is not accurate.

### Environmental Conditions

Visibility conditions:

```{r}
#| echo: false
#| warning: false
effort_mar$VISIBIL <- gsub("5-Feb", "2-5", effort_mar$VISIBIL)
effort_mar$VISIBIL <- gsub("2-Jan", "1-2", effort_mar$VISIBIL)
#visibility conditions
#print(unique(effort$VISIBIL))
#monitoring effort with >5 km visibiilIty 
effort_highvis <- filter(effort_mar, VISIBIL == ">5")
effort_high <- hms(effort_highvis$VIS_DAY_OBS) %>% period_to_seconds()
effort_high <- (((sum(effort_high, na.rm=TRUE))/60)/60)
effort_high_PV <- hms(effort_highvis$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_high_PV <- (((sum(effort_high_PV, na.rm=TRUE))/60)/60)
effort_night <- hms(effort_highvis$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_night <- (((sum(effort_night, na.rm=TRUE))/60)/60)

greater_five <- (effort_high + effort_high_PV + effort_night)

effort_midvis <- filter(effort_mar, VISIBIL == "2-5")
effort_midvis_day <- hms(effort_midvis$VIS_DAY_OBS) %>% period_to_seconds()
effort_midvis_day <- (((sum(effort_midvis_day, na.rm=TRUE))/60)/60)
effort_midvis_night <- hms(effort_midvis$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_midvis_night <- (((sum(effort_midvis_night, na.rm=TRUE))/60)/60)
effort_midvis_PV <- hms(effort_midvis$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_midvis_PV <- (((sum(effort_midvis_PV, na.rm=TRUE))/60)/60)
effort_midvis_P <- hms(effort_midvis$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_midvis_P <- (((sum(effort_midvis_P, na.rm=TRUE))/60)/60)

two_to_five <- (effort_midvis_day + effort_midvis_night + effort_midvis_P + effort_midvis_PV)

effort_lowvis <- filter(effort_mar, VISIBIL == "0.5-1" | VISIBIL == "1-2" | VISIBIL == "0.05-0.1" |
                          VISIBIL == "0.3-0.5" | VISIBIL == "<.05" |VISIBIL == "0.1-0.3" )
effort_lowvis_day <- hms(effort_lowvis$VIS_DAY_OBS) %>% period_to_seconds()
effort_lowvis_day <- (((sum(effort_lowvis_day, na.rm=TRUE))/60)/60)
effort_lowvis_night <- hms(effort_lowvis$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_lowvis_night <- (((sum(effort_lowvis_night, na.rm=TRUE))/60)/60)
effort_lowvis_PV <- hms(effort_lowvis$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_lowvis_PV <- (((sum(effort_lowvis_PV, na.rm=TRUE))/60)/60)
effort_lowvis_P <- hms(effort_lowvis$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_lowvis_P <- (((sum(effort_lowvis_P, na.rm=TRUE))/60)/60)

less_than_2 <- (effort_lowvis_P + effort_lowvis_PV + effort_lowvis_night + effort_lowvis_day)

Visibility <- c("Greater than 5 km", "2 to 5 km", "Less than 2 km")
Duration <- c(greater_five, two_to_five, less_than_2) %>% round(digits=2)
df<- data.frame(Visibility=Visibility, Duration=Duration)
  
visibility_table <- gt(df) %>% cols_label(Visibility = "Visibility", Duration= "Duration (HH.HH)")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
visibility_table
```

Swell height during monitoring:

```{r}
#| echo: false
#| warning: false
effort_mar$SWELL <- gsub("4-Feb", "2-4", effort_mar$SWELL)
lowswell <- filter(effort_mar, SWELL == "<2")
s_day <- hms(lowswell$VIS_DAY_OBS) %>% period_to_seconds()
s_day <- (((sum(s_day, na.rm=TRUE))/60)/60)
s_night <- hms(lowswell$VIS_NIGHT_OBS) %>% period_to_seconds()
s_night <- (((sum(s_night, na.rm=TRUE))/60)/60)
s_PAM <- hms(lowswell$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
s_PAM <- (((sum(s_PAM, na.rm=TRUE))/60)/60)
d_PAM <- hms(lowswell$VIS_PAM_DAY_OBS) %>% period_to_seconds()
d_PAM <- (((sum(d_PAM, na.rm=TRUE))/60)/60)
low_swell <- (s_day + s_night + s_PAM + d_PAM)
#swell 2-4 meters- 143.08 hrs
midswell <- filter(effort_mar, SWELL == "2-4")
m_day <- hms(midswell$VIS_DAY_OBS) %>% period_to_seconds()
m_day <- (((sum(m_day, na.rm=TRUE))/60)/60)
m_night <- hms(midswell$VIS_NIGHT_OBS) %>% period_to_seconds()
m_night <- (((sum(m_night, na.rm=TRUE))/60)/60)
m_PAM <- hms(midswell$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
m_PAM <- (((sum(m_PAM, na.rm=TRUE))/60)/60)
mid_swell <- (m_day + m_night + m_PAM)

Swell = c("Less than 2 m", "2 to 4 m")
Duration <- c(low_swell, mid_swell)%>% round(digits=2)
df<- data.frame(Swell=Swell, Duration=Duration)
  
Swell_table <- gt(df) %>% cols_label(Swell = "Swell", Duration= "Duration (HH.HH)")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
Swell_table
```

Beaufort Sea State during monitoring:

```{r}
#| echo: false
#| warning: false

#Beaufort Sea State during monitoring
#B1 
effort_B1 <- filter(effort_mar, BEAUF == 1)
effort_B1_day <- hms(effort_B1$VIS_DAY_OBS) %>% period_to_seconds()
effort_B1_day <- (((sum(effort_B1_day, na.rm=TRUE))/60)/60)
effort_B1_night <- hms(effort_B1$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B1_night <- (((sum(effort_B1_night, na.rm=TRUE))/60)/60)
effort_B1_PAM <- hms(effort_B1$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B1_PAM <- (((sum(effort_B1_PAM, na.rm=TRUE))/60)/60)
b1 <- (effort_B1_day + effort_B1_night + effort_B1_PAM)
#B2
effort_B2 <- filter(effort_mar, BEAUF == 2)
effort_B2_day <- hms(effort_B2$VIS_DAY_OBS) %>% period_to_seconds()
effort_B2_day <- (((sum(effort_B2_day, na.rm=TRUE))/60)/60)
effort_B2_night <- hms(effort_B2$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B2_night <- (((sum(effort_B2_night, na.rm=TRUE))/60)/60)
effort_B2_PAM <- hms(effort_B2$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B2_PAM <- (((sum(effort_B2_PAM, na.rm=TRUE))/60)/60)
b2 <- (effort_B2_day + effort_B2_night + effort_B2_PAM)
#B3
effort_B3 <- filter(effort_mar, BEAUF == 3)
effort_B3_day <- hms(effort_B3$VIS_DAY_OBS) %>% period_to_seconds()
effort_B3_day <- (((sum(effort_B3_day, na.rm=TRUE))/60)/60)
effort_B3_night <- hms(effort_B3$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B3_night <- (((sum(effort_B3_night, na.rm=TRUE))/60)/60)
effort_B3_PAM <- hms(effort_B3$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B3_PAM <- (((sum(effort_B3_PAM, na.rm=TRUE))/60)/60)
effort_B3_PAM_d <- hms(effort_B3$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_B3_PAM_d <- (((sum(effort_B3_PAM_d, na.rm=TRUE))/60)/60)
b3<-(effort_B3_day + effort_B3_night + effort_B3_PAM+effort_B3_PAM_d)
#B4
effort_B4 <- filter(effort_mar, BEAUF == 4)
effort_B4_day <- hms(effort_B4$VIS_DAY_OBS) %>% period_to_seconds()
effort_B4_day <- (((sum(effort_B4_day, na.rm=TRUE))/60)/60)
effort_B4_night <- hms(effort_B4$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B4_night <- (((sum(effort_B4_night, na.rm=TRUE))/60)/60)
effort_B4_PAM <- hms(effort_B4$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B4_PAM <- (((sum(effort_B4_PAM, na.rm=TRUE))/60)/60)
b4<-(effort_B4_day + effort_B4_night + effort_B4_PAM)
#B5
effort_B5 <- filter(effort_mar, BEAUF == 5)
effort_B5_day <- hms(effort_B5$VIS_DAY_OBS) %>% period_to_seconds()
effort_B5_day <- (((sum(effort_B5_day, na.rm=TRUE))/60)/60)
effort_B5_night <- hms(effort_B5$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B5_night <- (((sum(effort_B5_night, na.rm=TRUE))/60)/60)
effort_B5_PAM <- hms(effort_B5$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B5_PAM <- (((sum(effort_B5_PAM, na.rm=TRUE))/60)/60)
b5<-(effort_B5_day + effort_B5_night + effort_B5_PAM)
#B6
effort_B6 <- filter(effort_mar, BEAUF == 6)
effort_B6_day <- hms(effort_B6$VIS_DAY_OBS) %>% period_to_seconds()
effort_B6_day <- (((sum(effort_B6_day, na.rm=TRUE))/60)/60)
effort_B6_night <- hms(effort_B6$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B6_night <- (((sum(effort_B6_night, na.rm=TRUE))/60)/60)
effort_B6_PAM <- hms(effort_B6$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B6_PAM <- (((sum(effort_B6_PAM, na.rm=TRUE))/60)/60)
b6<-(effort_B6_day + effort_B6_night + effort_B6_PAM)

Beaufort = c("B1", "B2", "B3", "B4", "B5", "B6")
Duration <- c(b1, b2, b3, b4, b5, b6)%>% round(digits=2)
df<- data.frame(Beaufort=Beaufort, Duration=Duration)
  
Beauf_table <- gt(df) %>% cols_label(Beaufort = "Beaufort Sea State", Duration= "Duration (HH.HH)")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
Beauf_table
```

### Visual Detections

Total number of detection events by species:

```{r}
#| echo: false
#| warning: false

visualdetect_Marc <- visualdetect %>% filter(VESSEL == "Marcelle Bordelon") %>% filter(PROJECT_NUMBER == 222076)

#detections by species
species_summary <- visualdetect_Marc %>%
  count(NAME_COMMON)
species_table <- gt(species_summary) %>% cols_label(NAME_COMMON = "Species",
                                          n = "Number of detection records")%>% tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
species_table
```

Total detected individuals by species:

```{r}
#| echo: false
#| warning: false
individuals_summary <- visualdetect_Marc %>%
  group_by(NAME_COMMON) %>%
  summarize(
    total_value = sum(TOT_NUM),
            average_value = round(mean(TOT_NUM),1),
            dist_value = round(mean(RANGE_VESSEL_START),0))

ind_table <- gt(individuals_summary) %>% cols_label(NAME_COMMON = "Species",
                  total_value = "Individuals Count",
                  average_value = "Average group size",
                  dist_value = "Average distance (m) at first detection")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )

ind_table
```

Closest point of approach (CPA) to source (sparker) during detections:

```{r}
#| echo: false
#| warning: false
visualdetect_Marc$MITZONE_SILENTSOURCE_DIST <- as.numeric(visualdetect_Marc$MITZONE_SILENTSOURCE_DIST)
CPA <- visualdetect_Marc %>%
  group_by(NAME_COMMON) %>%
  summarize(active_value = round(mean(MITZONE_ACTIVESOURCE_DIST, na.rm = TRUE),2),
            inactive_value = round(mean(MITZONE_SILENTSOURCE_DIST, na.rm = TRUE),2))


CPA_table <- gt(CPA) %>% cols_label(NAME_COMMON = "Species",
                  active_value = "Mean CPA to active sparker (meters)",
                  inactive_value = "Mean CPA to silent sparker (meters)") %>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )

CPA_table
```

### Incidental Harassment Authorization (IHA) Level B Exposures

IHA Level B exposures during the survey:

```{r}
#| echo: false
#| warning: false

take <- visualdetect_Marc %>%
  group_by(NAME_COMMON) %>%
  summarize(take_value = sum(LEVELB_TAKE, na.rm = TRUE))


take_table <- gt(take) %>% cols_label(NAME_COMMON = "Species",
take_value = "Total Number of Animals Observed Inside the Level B Harassment Zone") %>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )

take_table
```

### Acoustic Detections

Acoustic detections during the survey:

```{r}
#| echo: false
#| warning: false

acousdetect_Marc <- acousticdetect %>% filter(VESSEL == "Marcelle Bordelon") %>% filter(PROJECT_NUMBER == 222076)
acousdetect_Marc$MITZONE_SILENTSOURCE_DIST <- as.numeric(acousdetect_Marc$MITZONE_SILENTSOURCE_DIST )

acousdetections <- acousdetect_Marc %>%
  group_by(NAME_COMMON) %>%
  summarize(active_value = round(mean(MITZONE_ACTIVESOURCE_DIST, na.rm = TRUE),2),
            inactive_value = round(mean(MITZONE_SILENTSOURCE_DIST, na.rm = TRUE),2), total_value = sum(ANIMAL_BEST))



acoustic_table <- gt(acousdetections) %>% cols_label(NAME_COMMON = "Species",
active_value = "CPA when sparker was active", inactive_value = "CPA when sparker was inactive", total_value = "Estimated total number of individuals detected") %>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )

acoustic_table
```

### Port Calls

Port calls during the survey:

```{r}
#| echo: false
#| warning: false
portcall_m <- portcall %>% filter(VESSEL == "Marcelle Bordelon") %>% filter(PROJECT_NUMBER == 222076)


portcall_table <- gt(portcall_m)%>% cols_label(PROJECT_NUMBER = "Project Number", VESSEL = "Vessel", DATE = "Date", TIME = "Time", PORT = "Port", ACTION = "Action", COMMENT_PORT_CALL= "Comments") %>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )

portcall_table
```

## Project 219236 (*Miss Emma McCall*)

### Operation Activity

Total hours of sparker activity:

```{r}
#| echo: false
#| warning: false

setwd('C:/Users/nicole.mucci/Documents/R/PEMAD-MDEB-PSO')
#load libraries
library(readr)
library(tidyverse)
library(dplyr)
library(tidyr)
library(stringr)
library(lubridate)
operations <- readr::read_csv("data/Attentive/Attentive2023_Operations_Tidy.csv")
visualdetect<- readr::read_csv("data/Attentive/Attentive2023_VisualDetect_Tidy.csv")
effort <- readr::read_csv("data/Attentive/Attentive2023_Effort_Tidy.csv")
operations <- readr::read_csv("data/Attentive/Attentive2023_Operations_Tidy.csv")
portcall <- readr::read_csv("data/Attentive/Attentive2023_PortCall_Tidy.csv")
acousticdetect <- readr::read_csv("data/Attentive/Attentive2023_AcousticDetect_Tidy.csv")
portcall <- readr::read_csv("data/Attentive/Attentive2023_PortCall_Tidy.csv", locale = locale(encoding = "latin1"))
operations_emma <- operations %>% filter(VESSEL == "Emma McCall") %>% filter(PROJECT_NUMBER == 219236)

sparker_sursource <- operations_emma %>% hms(operations_emma$DUR_SURSOURCE) %>% period_to_seconds()
sparker_sursource <- (((sum(sparker_sursource, na.rm=TRUE))/60)/60)

sparker_soft <- operations_emma %>% hms(operations_emma$DUR_SOFTSTART) %>% period_to_seconds()
sparker_soft <- (((sum(sparker_soft, na.rm=TRUE))/60)/60)

sparker_test <- operations_emma %>% hms(operations_emma$DUR_TEST) %>% period_to_seconds()
sparker_test <- (((sum(sparker_test, na.rm=TRUE))/60)/60)

sparker_presursource <- operations_emma %>% hms(operations_emma$DUR_PRESURSOURCE) %>% period_to_seconds()
sparker_presursource <- (((sum(sparker_presursource, na.rm=TRUE))/60)/60)

sparker_postsur <- operations_emma %>% hms(operations_emma$DUR_POSTSUR) %>% period_to_seconds()
sparker_postsur <- (((sum(sparker_postsur, na.rm=TRUE))/60)/60)

sparker_reduced <- operations_emma %>% hms(operations_emma$DUR_REDUCEDOUTPUT) %>% period_to_seconds()
sparker_reduced <- (((sum(sparker_reduced, na.rm=TRUE))/60)/60)

sparker_eq <- operations_emma %>% hms(operations_emma$DUR_EQUIP_RET) %>% period_to_seconds()
sparker_eq <- (((sum(sparker_eq, na.rm=TRUE))/60)/60)

total_sparkerop <- sum(sparker_sursource, sparker_soft, sparker_test, sparker_presursource, sparker_postsur, sparker_reduced, sparker_eq)

vessel <- c("Miss Emma McCall")
date <- c("6/23/2023 - 1/2/2024")
operation <- c(total_sparkerop)%>% round(digits=2)
df <- data.frame(vessel = vessel, date=date, operation = operation)

op_table <- gt(df) %>% cols_label(vessel = "Survey Vessel", date= "Dates of Operation", operation= "Total Hours of Source Operation (HH.HH)")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
op_table
```

### Monitoring Effort

Summary of monitoring effort:

\[THIS NEEDS TO BE FIXED\]

```{r}
#| echo: false
#| warning: false

setwd('C:/Users/nicole.mucci/Documents/R/PEMAD-MDEB-PSO')
effort <- readr::read_csv("data/Attentive/Attentive2023_Effort_Tidy.csv")
effort_emma <- effort %>% filter(VESSEL == "Emma McCall") %>% filter(PROJECT_NUMBER == 219236)

effort_emma$SOURCE_DAY_OBS <- hms::as_hms(effort_emma$SOURCE_DAY_OBS)

day_obs <- hms(effort_emma$VIS_DAY_OBS)
night_obs <- hms(effort_emma$VIS_NIGHT_OBS)
acous_obs <- hms(effort_emma$VIS_PAM_NIGHT_OBS)
day_obs_sec <- period_to_seconds(day_obs)
day_obs_hrs <- (((sum(day_obs_sec, na.rm=TRUE))/60)/60)
#sparkers active 
sparkers_day <- hms(effort_emma$SOURCE_DAY_OBS)
sparkers_day_sec <- period_to_seconds(sparkers_day)
sparkers_day_hrs <- (((sum(sparkers_day_sec, na.rm=TRUE))/60)/60)
sparkers_nite <- hms(effort_emma$SOURCE_NIGHT_OBS)
sparkers_nite_sec <- period_to_seconds(sparkers_nite)
sparkers_nite_hrs <- (((sum(sparkers_nite_sec, na.rm=TRUE))/60)/60)
sparkers_day_pam <- hms(effort_emma$SOURCE_VIS_PAM_DAY)
sparkers_day_pam_sec <- period_to_seconds(sparkers_day_pam)
sparkers_day_pam_hrs <- (((sum(sparkers_day_pam_sec, na.rm=TRUE))/60)/60)
sparkers_nite_pam <- hms(effort_emma$SOURCE_VIS_PAM_NIGHT)
sparkers_nite_pam_sec <- period_to_seconds(sparkers_nite_pam)
sparkers_nite_pam_hrs <- (((sum(sparkers_nite_pam_sec, na.rm=TRUE))/60)/60)
sparkers_active <- sum(sparkers_nite_hrs + sparkers_day_hrs + sparkers_nite_pam_hrs+ sparkers_day_pam_hrs)

sdp <- hms(effort_emma$SOURCE_VIS_PAM_DAY)
sdp_sec <- period_to_seconds(sdp)
sdp_hrs <- (((sum(sdp_sec, na.rm=TRUE))/60)/60)

#PAM daytime and nighttime
pam_day<- hms(effort_emma$VIS_PAM_DAY_OBS)
pam_day_sec <- period_to_seconds(pam_day)
pam_day_hrs <- (((sum(pam_day_sec, na.rm=TRUE))/60)/60)
pam_night<- hms(effort_emma$VIS_PAM_NIGHT_OBS)
pam_night_sec <- period_to_seconds(pam_night)
pam_night_hrs <- (((sum(pam_night_sec , na.rm=TRUE))/60)/60)
night_obs_sec <- period_to_seconds(night_obs)
night_obs_hrs <- (((sum(night_obs_sec, na.rm=TRUE))/60)/60)
acous_obs_sec <- period_to_seconds(acous_obs)
acous_obs_hrs <- (((sum(acous_obs_sec, na.rm=TRUE))/60)/60)
total_day <- day_obs_hrs + pam_day_hrs
total_night <- night_obs_hrs + pam_night_hrs
total_vis <- total_day + total_night
total_pam <- pam_day_hrs + pam_night_hrs
total_obs <- (day_obs_hrs + night_obs_hrs + total_pam)

monitoring <- c("Sparker active", "Sparker not active", "Daytime", "Nighttime", "Total")
visual <- c(1, 1,total_day, total_night, total_obs) %>% round(digits = 2)
PAM <- c(1, 1, pam_day_hrs, pam_night_hrs, total_pam) %>% round(digits = 2)

df <- data.frame(Monitoring=monitoring, Visual = visual, PAM= PAM)

monitoring_table <- gt(df) %>% tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
monitoring_table
```

### Environmental Conditions

Visibility conditions:

```{r}
#| echo: false
#| warning: false
effort_emma$VISIBIL <- gsub("5-Feb", "2-5", effort_emma$VISIBIL)
effort_emma$VISIBIL <- gsub("2-Jan", "1-2", effort_emma$VISIBIL)
#visibility conditions
#print(unique(effort_emma$VISIBIL))
#monitoring effort with >5 km visibiilIty 
effort_highvis <- filter(effort_emma, VISIBIL == ">5")
effort_high <- hms(effort_highvis$VIS_DAY_OBS) %>% period_to_seconds()
effort_high <- (((sum(effort_high, na.rm=TRUE))/60)/60)
effort_high_PV <- hms(effort_highvis$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_high_PV <- (((sum(effort_high_PV, na.rm=TRUE))/60)/60)
effort_night <- hms(effort_highvis$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_night <- (((sum(effort_night, na.rm=TRUE))/60)/60)
effort_high_P <- hms(effort_highvis$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_high_P <- (((sum(effort_high_P, na.rm=TRUE))/60)/60)
greater_five <- (effort_high + effort_high_PV + effort_night + effort_high_P)

effort_midvis <- filter(effort_emma, VISIBIL == "2-5")
effort_midvis_day <- hms(effort_midvis$VIS_DAY_OBS) %>% period_to_seconds()
effort_midvis_day <- (((sum(effort_midvis_day, na.rm=TRUE))/60)/60)
effort_midvis_night <- hms(effort_midvis$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_midvis_night <- (((sum(effort_midvis_night, na.rm=TRUE))/60)/60)
effort_midvis_PV <- hms(effort_midvis$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_midvis_PV <- (((sum(effort_midvis_PV, na.rm=TRUE))/60)/60)
effort_midvis_P <- hms(effort_midvis$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_midvis_P <- (((sum(effort_midvis_P, na.rm=TRUE))/60)/60)

two_to_five <- (effort_midvis_day + effort_midvis_night + effort_midvis_P + effort_midvis_PV)

effort_lowvis <- filter(effort_emma, VISIBIL == "0.5-1" | VISIBIL == "1-2" | VISIBIL == "0.05-0.1" |
                          VISIBIL == "0.3-0.5" | VISIBIL == "<.05" |VISIBIL == "0.1-0.3" )
effort_lowvis_day <- hms(effort_lowvis$VIS_DAY_OBS) %>% period_to_seconds()
effort_lowvis_day <- (((sum(effort_lowvis_day, na.rm=TRUE))/60)/60)
effort_lowvis_night <- hms(effort_lowvis$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_lowvis_night <- (((sum(effort_lowvis_night, na.rm=TRUE))/60)/60)
effort_lowvis_PV <- hms(effort_lowvis$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_lowvis_PV <- (((sum(effort_lowvis_PV, na.rm=TRUE))/60)/60)
effort_lowvis_P <- hms(effort_lowvis$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_lowvis_P <- (((sum(effort_lowvis_P, na.rm=TRUE))/60)/60)

less_than_2 <- (effort_lowvis_P + effort_lowvis_PV + effort_lowvis_night + effort_lowvis_day)

Visibility <- c("Greater than 5 km", "2 to 5 km", "Less than 2 km")
Duration <- c(greater_five, two_to_five, less_than_2) %>% round(digits=2)
df<- data.frame(Visibility=Visibility, Duration=Duration)
  
visibility_table <- gt(df) %>% cols_label(Visibility = "Visibility", Duration= "Duration (HH.HH)")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
visibility_table
```

Swell height during monitoring:

```{r}
#| echo: false
#| warning: false
effort_emma$SWELL <- gsub("4-Feb", "2-4", effort_emma$SWELL)
lowswell <- filter(effort_emma, SWELL == "<2")
s_day <- hms(lowswell$VIS_DAY_OBS) %>% period_to_seconds()
s_day <- (((sum(s_day, na.rm=TRUE))/60)/60)
s_night <- hms(lowswell$VIS_NIGHT_OBS) %>% period_to_seconds()
s_night <- (((sum(s_night, na.rm=TRUE))/60)/60)
s_PAM <- hms(lowswell$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
s_PAM <- (((sum(s_PAM, na.rm=TRUE))/60)/60)
d_PAM <- hms(lowswell$VIS_PAM_DAY_OBS) %>% period_to_seconds()
d_PAM <- (((sum(d_PAM, na.rm=TRUE))/60)/60)
low_swell <- (s_day + s_night + s_PAM + d_PAM)
#swell 2-4 meters- 143.08 hrs
midswell <- filter(effort_emma, SWELL == "2-4")
m_day <- hms(midswell$VIS_DAY_OBS) %>% period_to_seconds()
m_day <- (((sum(m_day, na.rm=TRUE))/60)/60)
m_night <- hms(midswell$VIS_NIGHT_OBS) %>% period_to_seconds()
m_night <- (((sum(m_night, na.rm=TRUE))/60)/60)
m_PAM <- hms(midswell$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
m_PAM <- (((sum(m_PAM, na.rm=TRUE))/60)/60)
mid_swell <- (m_day + m_night + m_PAM)

Swell = c("Less than 2 m", "2 to 4 m")
Duration <- c(low_swell, mid_swell)%>% round(digits=2)
df<- data.frame(Swell=Swell, Duration=Duration)
  
Swell_table <- gt(df) %>% cols_label(Swell = "Swell", Duration= "Duration (HH.HH)")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
Swell_table
```

Beaufort Sea State during monitoring:

```{r}
#| echo: false
#| warning: false

#Beaufort Sea State during monitoring
#B1 
effort_B1 <- filter(effort_emma, BEAUF == 1)
effort_B1_day <- hms(effort_B1$VIS_DAY_OBS) %>% period_to_seconds()
effort_B1_day <- (((sum(effort_B1_day, na.rm=TRUE))/60)/60)
effort_B1_night <- hms(effort_B1$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B1_night <- (((sum(effort_B1_night, na.rm=TRUE))/60)/60)
effort_B1_PAM <- hms(effort_B1$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B1_PAM <- (((sum(effort_B1_PAM, na.rm=TRUE))/60)/60)
effort_B1_P <- hms(effort_B1$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_B1_P <- (((sum(effort_B1_P, na.rm=TRUE))/60)/60)
b1 <- (effort_B1_day + effort_B1_night + effort_B1_PAM + effort_B1_P)
#B2
effort_B2 <- filter(effort_emma, BEAUF == 2)
effort_B2_day <- hms(effort_B2$VIS_DAY_OBS) %>% period_to_seconds()
effort_B2_day <- (((sum(effort_B2_day, na.rm=TRUE))/60)/60)
effort_B2_night <- hms(effort_B2$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B2_night <- (((sum(effort_B2_night, na.rm=TRUE))/60)/60)
effort_B2_PAM <- hms(effort_B2$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B2_PAM <- (((sum(effort_B2_PAM, na.rm=TRUE))/60)/60)
effort_B2_P <- hms(effort_B2$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_B2_P <- (((sum(effort_B2_P, na.rm=TRUE))/60)/60)
b2 <- (effort_B2_day + effort_B2_night + effort_B2_PAM +effort_B2_P)
#B3
effort_B3 <- filter(effort_emma, BEAUF == 3)
effort_B3_day <- hms(effort_B3$VIS_DAY_OBS) %>% period_to_seconds()
effort_B3_day <- (((sum(effort_B3_day, na.rm=TRUE))/60)/60)
effort_B3_night <- hms(effort_B3$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B3_night <- (((sum(effort_B3_night, na.rm=TRUE))/60)/60)
effort_B3_PAM <- hms(effort_B3$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B3_PAM <- (((sum(effort_B3_PAM, na.rm=TRUE))/60)/60)
effort_B3_PAM_d <- hms(effort_B3$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_B3_PAM_d <- (((sum(effort_B3_PAM_d, na.rm=TRUE))/60)/60)
b3<-(effort_B3_day + effort_B3_night + effort_B3_PAM+effort_B3_PAM_d)
#B4
effort_B4 <- filter(effort_emma, BEAUF == 4)
effort_B4_day <- hms(effort_B4$VIS_DAY_OBS) %>% period_to_seconds()
effort_B4_day <- (((sum(effort_B4_day, na.rm=TRUE))/60)/60)
effort_B4_night <- hms(effort_B4$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B4_night <- (((sum(effort_B4_night, na.rm=TRUE))/60)/60)
effort_B4_PAM <- hms(effort_B4$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B4_PAM <- (((sum(effort_B4_PAM, na.rm=TRUE))/60)/60)
b4<-(effort_B4_day + effort_B4_night + effort_B4_PAM)
#B5
effort_B5 <- filter(effort_emma, BEAUF == 5)
effort_B5_day <- hms(effort_B5$VIS_DAY_OBS) %>% period_to_seconds()
effort_B5_day <- (((sum(effort_B5_day, na.rm=TRUE))/60)/60)
effort_B5_night <- hms(effort_B5$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B5_night <- (((sum(effort_B5_night, na.rm=TRUE))/60)/60)
effort_B5_PAM <- hms(effort_B5$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B5_PAM <- (((sum(effort_B5_PAM, na.rm=TRUE))/60)/60)
b5<-(effort_B5_day + effort_B5_night + effort_B5_PAM)
#B6
effort_B6 <- filter(effort_emma, BEAUF == 6)
effort_B6_day <- hms(effort_B6$VIS_DAY_OBS) %>% period_to_seconds()
effort_B6_day <- (((sum(effort_B6_day, na.rm=TRUE))/60)/60)
effort_B6_night <- hms(effort_B6$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B6_night <- (((sum(effort_B6_night, na.rm=TRUE))/60)/60)
effort_B6_PAM <- hms(effort_B6$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B6_PAM <- (((sum(effort_B6_PAM, na.rm=TRUE))/60)/60)
b6<-(effort_B6_day + effort_B6_night + effort_B6_PAM)

effort_B7 <- filter(effort_emma, BEAUF == 7)
effort_B7_day <- hms(effort_B7$VIS_DAY_OBS) %>% period_to_seconds()
effort_B7_day <- (((sum(effort_B7_day, na.rm=TRUE))/60)/60)
effort_B7_night <- hms(effort_B7$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B7_night <- (((sum(effort_B7_night, na.rm=TRUE))/60)/60)
effort_B7_PAM <- hms(effort_B7$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B7_PAM <- (((sum(effort_B7_PAM, na.rm=TRUE))/60)/60)
b7<-(effort_B7_day + effort_B7_night + effort_B7_PAM)

effort_B8 <- filter(effort_emma, BEAUF == 8)
effort_B8_day <- hms(effort_B8$VIS_DAY_OBS) %>% period_to_seconds()
effort_B8_day <- (((sum(effort_B8_day, na.rm=TRUE))/60)/60)
effort_B8_night <- hms(effort_B8$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B8_night <- (((sum(effort_B8_night, na.rm=TRUE))/60)/60)
effort_B8_PAM <- hms(effort_B8$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B8_PAM <- (((sum(effort_B8_PAM, na.rm=TRUE))/60)/60)
b8<-(effort_B8_day + effort_B8_night + effort_B8_PAM)


Beaufort = c("B1", "B2", "B3", "B4", "B5", "B6", "B7", "B6")
Duration <- c(b1, b2, b3, b4, b5, b6, b7, b8)%>% round(digits=2)
df<- data.frame(Beaufort=Beaufort, Duration=Duration)
  
Beauf_table <- gt(df) %>% cols_label(Beaufort = "Beaufort Sea State", Duration= "Duration (HH.HH)")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
Beauf_table
```

### Visual Detections

Total number of detection events by species:

\[MEAN GROUP SIZE OF HUMPBACK WHALE DIFFERENT FROM WHAT WAS REPORTED\]

```{r}
#| echo: false
#| warning: false
visualdetect_emma <- visualdetect %>% filter(VESSEL == "Emma McCall") %>% filter(PROJECT_NUMBER == 219236)

individuals_summary <- visualdetect_emma %>%
  group_by(NAME_COMMON) %>%
  summarize(
    total_value = sum(TOT_NUM),
            average_value = round(mean(TOT_NUM),1),
            dist_value = round(mean(RANGE_VESSEL_START),0))

ind_table <- gt(individuals_summary) %>% cols_label(NAME_COMMON = "Species",
                  total_value = "Individuals Count",
                  average_value = "Average group size",
                  dist_value = "Average distance (m) at first detection")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )

ind_table
```

Closest point of approach (CPA) to sparker:

\[CPA TO SILENT SPARKER OF COMMON DOLPHIN DIFFERENT FROM WHAT WAS REPORTED\]

```{r}
#| echo: false
#| warning: false
visualdetect_emma$MITZONE_SILENTSOURCE_DIST <- as.numeric(visualdetect_emma$MITZONE_SILENTSOURCE_DIST)

CPA <- visualdetect_emma %>%
  group_by(NAME_COMMON) %>%
  summarize(active_value = round(mean(MITZONE_ACTIVESOURCE_DIST, na.rm = TRUE),2),
            inactive_value = round(mean(MITZONE_SILENTSOURCE_DIST, na.rm = TRUE),2))


CPA_table <- gt(CPA) %>% cols_label(NAME_COMMON = "Species",
                  active_value = "Mean CPA to active sparker (meters)",
                  inactive_value = "Mean CPA to silent sparker (meters)") %>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )

CPA_table
```

### Incidental Harassment Authorization (IHA) Level B Exposures

IHA Level B exposures during the survey:

```{r}
#| echo: false 
#| warning: false  
 
take <- visualdetect_emma %>% group_by(NAME_COMMON) %>%   
  summarize(take_value = sum(LEVELB_TAKE, na.rm = TRUE))   

take_table <- gt(take) %>% cols_label(NAME_COMMON = "Species", take_value = "Total Number of Animals Observed Inside the Level B Harassment Zone") %>%  tab_options(     data_row.padding = px(1),     table.align = "left"   )  

take_table
```

### Acoustic Detections

Acoustic detections during the survey:

```{r}
#| echo: false
#| warning: false

acousdetect_emma <- acousticdetect %>% filter(VESSEL == "Emma McCall") %>% filter(PROJECT_NUMBER == 219236)
acousdetect_emma$MITZONE_SILENTSOURCE_DIST <- as.numeric(acousdetect_emma$MITZONE_SILENTSOURCE_DIST )

acousdetections <- acousdetect_emma %>%
  group_by(NAME_COMMON) %>%
  summarize(active_value = round(mean(MITZONE_ACTIVESOURCE_DIST, na.rm = TRUE),2),
            inactive_value = round(mean(MITZONE_SILENTSOURCE_DIST, na.rm = TRUE),2), total_value = sum(ANIMAL_BEST))



acoustic_table <- gt(acousdetections) %>% cols_label(NAME_COMMON = "Species",
active_value = "CPA when sparker was active", inactive_value = "CPA when sparker was inactive", total_value = "Estimated total number of individuals detected") %>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )

acoustic_table
```

### Port Calls

Port calls during the survey:

```{r}
#| echo: false
#| warning: false

portcall_em <- portcall %>% filter(VESSEL == "Emma McCall") %>% filter(PROJECT_NUMBER == 219236)


portcall_table <- gt(portcall_em)%>% cols_label(PROJECT_NUMBER = "Project Number", VESSEL = "Vessel", DATE = "Date", TIME = "Time", PORT = "Port", ACTION = "Action", COMMENT_PORT_CALL= "Comments") %>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )

portcall_table
```

## Project 222794 (*Miss Emma McCall*) and Project 219236 (*Marcelle Bordelon*)

### Operation Activity

Total hours of sparker operation:

```{r}
#| echo: false
#| warning: false

setwd('C:/Users/nicole.mucci/Documents/R/PEMAD-MDEB-PSO')
#load libraries
library(readr)
library(tidyverse)
library(dplyr)
library(tidyr)
library(stringr)
library(gt)

visualdetect<- readr::read_csv("data/Attentive/Attentive2023_VisualDetect_Tidy.csv")
effort <- readr::read_csv("data/Attentive/Attentive2023_Effort_Tidy.csv")
operations <- readr::read_csv("data/Attentive/Attentive2023_Operations_Tidy.csv")
portcall <- readr::read_csv("data/Attentive/Attentive2023_PortCall_Tidy.csv")
acousticdetect <- readr::read_csv("data/Attentive/Attentive2023_AcousticDetect_Tidy.csv")
portcall <- readr::read_csv("data/Attentive/Attentive2023_PortCall_Tidy.csv", locale = locale(encoding = "latin1"))
oper_marc_emma <- operations %>% filter(VESSEL == "Emma McCall" & PROJECT_NUMBER == 222794 |VESSEL == "Marcelle Bordelon" & PROJECT_NUMBER == 219236)


sparker_sursource <- oper_marc_emma %>% hms(oper_marc_emma$DUR_SURSOURCE) %>% period_to_seconds()
sparker_sursource <- (((sum(sparker_sursource, na.rm=TRUE))/60)/60)

sparker_soft <- oper_marc_emma %>% hms(oper_marc_emma$DUR_SOFTSTART) %>% period_to_seconds()
sparker_soft <- (((sum(sparker_soft, na.rm=TRUE))/60)/60)

sparker_test <- oper_marc_emma %>% hms(oper_marc_emma$DUR_TEST) %>% period_to_seconds()
sparker_test <- (((sum(sparker_test, na.rm=TRUE))/60)/60)

sparker_presursource <- oper_marc_emma %>% hms(oper_marc_emma$DUR_PRESURSOURCE) %>% period_to_seconds()
sparker_presursource <- (((sum(sparker_presursource, na.rm=TRUE))/60)/60)

sparker_postsur <- oper_marc_emma %>% hms(oper_marc_emma$DUR_POSTSUR) %>% period_to_seconds()
sparker_postsur <- (((sum(sparker_postsur, na.rm=TRUE))/60)/60)

total_sparkerop <- sum(sparker_sursource, sparker_soft, sparker_test, sparker_presursource, sparker_postsur)

vessel <- c("Marcelle Bordelon", "Miss Emma McCall")
date <- c("12/26/2023 - 2/3/2024", "1/2/2024 - 2/12/2024")
operation <- c(total_sparkerop, 0)%>% round(digits=2)
df <- data.frame(vessel = vessel, date=date, operation = operation)

op_table <- gt(df) %>% cols_label(vessel = "Survey Vessel", date= "Dates of Operation", operation= "Total Hours of Source Operation (HH.HH)")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
op_table
```

### Monitoring Effort

```{r}
#| echo: false
#| warning: false

effort_em <- effort %>% filter(VESSEL == "Emma McCall" & PROJECT_NUMBER == 222794)
effort_marc <- effort %>% filter(VESSEL == "Marcelle Bordelon" & PROJECT_NUMBER == 219236)
#Emma McCall
day_obs_E <- hms(effort_em$VIS_DAY_OBS)
night_obs_E <- hms(effort_em$VIS_NIGHT_OBS)
acous_obs_E <- hms(effort_em$VIS_PAM_NIGHT_OBS)
day_obs_sec_E <- period_to_seconds(day_obs_E)
day_obs_hrs_E <- (((sum(day_obs_sec_E, na.rm=TRUE))/60)/60)
night_obs_sec_E <- period_to_seconds(night_obs_E)
night_obs_hrs_E <- (((sum(night_obs_sec_E, na.rm=TRUE))/60)/60)
total_E <- day_obs_hrs_E + night_obs_hrs_E
#Marcelle Bordelon
day_obs_M <- hms(effort_marc$VIS_DAY_OBS)
night_obs_M <- hms(effort_marc$VIS_NIGHT_OBS)
day_obs_sec_M <- period_to_seconds(day_obs_M)
day_obs_hrs_M <- (((sum(day_obs_sec_M, na.rm=TRUE))/60)/60)
night_obs_sec_M <- period_to_seconds(night_obs_M)
night_obs_hrs_M <- (((sum(night_obs_sec_M, na.rm=TRUE))/60)/60)
#PAM daytime and nighttime
pam_day_M<- hms(effort_marc$VIS_PAM_DAY_OBS)
pam_day_sec_M <- period_to_seconds(pam_day_M)
pam_day_hrs_M <- (((sum(pam_day_sec_M, na.rm=TRUE))/60)/60)
pam_night_M<- hms(effort_marc$VIS_PAM_NIGHT_OBS)
pam_night_sec_M <- period_to_seconds(pam_night_M)
pam_night_hrs_M <- (((sum(pam_night_sec_M , na.rm=TRUE))/60)/60)
night_total <- night_obs_hrs_M + pam_night_hrs_M
total_M <- night_total  + day_obs_hrs_M 

#sparkers active vs not active
sparkers_day <- (hms(effort_marc$SOURCE_DAY_OBS))
sparkers_day_sec <- period_to_seconds(sparkers_day)
sparkers_day_hrs <- (((sum(sparkers_day_sec, na.rm=TRUE))/60)/60)
sparkers_nite <- (hms(effort_marc$SOURCE_NIGHT_OBS))
sparkers_nite_sec <- period_to_seconds(sparkers_nite)
sparkers_nite_hrs <- (((sum(sparkers_nite_sec, na.rm=TRUE))/60)/60)

sparkers_nite_pam <- (hms(effort_marc$SOURCE_VIS_PAM_NIGHT))
sparkers_nite_pam_sec <- period_to_seconds(sparkers_nite_pam)
sparkers_nite_pam_hrs <- (((sum(sparkers_nite_pam_sec, na.rm=TRUE))/60)/60)
sparkers_active <- sum(sparkers_nite_hrs + sparkers_day_hrs + sparkers_nite_pam_hrs)

acous_obs_sec <- period_to_seconds(acous_obs)
acous_obs_hrs <- (((sum(acous_obs_sec, na.rm=TRUE))/60)/60)

```

Summary of monitoring effort:

```{r}
#| echo: false
#| warning: false

monitoring <- c("Sparker active", "Sparker not active", "Daytime", "Nighttime", "Total")
marcelle_visual <- c(sparkers_active, (total_M - sparkers_active ), day_obs_hrs_M,night_total,total_M) %>% round(digits=2)
marcelle_PAM <- c(sparkers_nite_pam_hrs,(pam_night_hrs_M-sparkers_nite_pam_hrs),pam_day_hrs_M,pam_night_hrs_M ,pam_night_hrs_M )%>% round(digits=2)
emma_visual <- c(0,total_E ,day_obs_hrs_E, night_obs_hrs_E,total_E ) %>% round(digits=2)
emma_PAM <- c(0,0,0,0,0)%>% round(digits=2)

df <- data.frame(Monitoring=monitoring, Visual = marcelle_visual, PAM= marcelle_PAM, Visual_1 = emma_visual, PAM_1= emma_PAM)

monitoring_table <- gt(df) %>% cols_label(Monitoring = "Monitoring effort", Visual= "Visual (HH.HH)", PAM= "PAM (HH.HH)", Visual_1= "Visual (HH.HH)", PAM_1= "PAM (HH.HH)") %>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  ) %>% tab_spanner(label= "RV Marcelle Bordelon", columns = c(Visual, PAM))%>% tab_spanner(label= "RV Miss Emma McCall", columns = c(Visual_1, PAM_1))
monitoring_table
```

### Environmental Conditions

Visibility conditions:

```{r}
#| echo: false
#| warning: false
setwd('C:/Users/nicole.mucci/Documents/R/PEMAD-MDEB-PSO')
effort <- readr::read_csv("data/Attentive/Attentive2023_Effort_Tidy.csv")
effort_marc_em <- effort %>% filter(VESSEL == "Emma McCall" & PROJECT_NUMBER == 222794 | VESSEL == "Marcelle Bordelon" & PROJECT_NUMBER == 219236)
#visibility conditions
effort_marc_em$VISIBIL <- gsub("5-Feb", "2-5", effort_marc_em$VISIBIL)
effort_marc_em$VISIBIL <- gsub("2-Jan", "1-2", effort_marc_em$VISIBIL)
#print(unique(effort_emma$VISIBIL))
#monitoring effort with >5 km visibiilIty = 2211.18 hrs
effort_highvis <- filter(effort_marc_em, VISIBIL == ">5")
effort_high <- hms(effort_highvis$VIS_DAY_OBS) %>% period_to_seconds()
effort_high <- (((sum(effort_high, na.rm=TRUE))/60)/60)
effort_high_PV <- hms(effort_highvis$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_high_PV <- (((sum(effort_high_PV, na.rm=TRUE))/60)/60)
effort_night <- hms(effort_highvis$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_night <- (((sum(effort_night, na.rm=TRUE))/60)/60)
effort_high_P <- hms(effort_highvis$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_high_P <- (((sum(effort_high_P, na.rm=TRUE))/60)/60)
greater_five <- (effort_high + effort_high_PV + effort_night + effort_high_P)

effort_midvis <- filter(effort_marc_em, VISIBIL == "2-5")
effort_midvis_day <- hms(effort_midvis$VIS_DAY_OBS) %>% period_to_seconds()
effort_midvis_day <- (((sum(effort_midvis_day, na.rm=TRUE))/60)/60)
effort_midvis_night <- hms(effort_midvis$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_midvis_night <- (((sum(effort_midvis_night, na.rm=TRUE))/60)/60)
effort_midvis_PV <- hms(effort_midvis$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_midvis_PV <- (((sum(effort_midvis_PV, na.rm=TRUE))/60)/60)
effort_midvis_P <- hms(effort_midvis$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_midvis_P <- (((sum(effort_midvis_P, na.rm=TRUE))/60)/60)

two_to_five <- (effort_midvis_day + effort_midvis_night + effort_midvis_P + effort_midvis_PV)

effort_lowvis <- filter(effort_marc_em, VISIBIL == "0.5-1" | VISIBIL == "1-2" | VISIBIL == "0.05-0.1" |
                          VISIBIL == "0.3-0.5" | VISIBIL == "<.05" |VISIBIL == "0.1-0.3" )
effort_lowvis_day <- hms(effort_lowvis$VIS_DAY_OBS) %>% period_to_seconds()
effort_lowvis_day <- (((sum(effort_lowvis_day, na.rm=TRUE))/60)/60)
effort_lowvis_night <- hms(effort_lowvis$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_lowvis_night <- (((sum(effort_lowvis_night, na.rm=TRUE))/60)/60)
effort_lowvis_PV <- hms(effort_lowvis$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_lowvis_PV <- (((sum(effort_lowvis_PV, na.rm=TRUE))/60)/60)
effort_lowvis_P <- hms(effort_lowvis$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_lowvis_P <- (((sum(effort_lowvis_P, na.rm=TRUE))/60)/60)

less_than_2 <- (effort_lowvis_P + effort_lowvis_PV + effort_lowvis_night + effort_lowvis_day)

Visibility <- c("Greater than 5 km", "2 to 5 km", "Less than 2 km")
Duration <- c(greater_five, two_to_five, less_than_2) %>% round(digits=2)
df<- data.frame(Visibility=Visibility, Duration=Duration)
  
visibility_table <- gt(df) %>% cols_label(Visibility = "Visibility", Duration= "Duration (HH.HH)")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
visibility_table
```

Swell height during monitoring:

```{r}
#| echo: false
#| warning: false

#print(unique(effort_marc_em$SWELL))
effort_marc_em$SWELL <- gsub("4-Feb", "2-4", effort_marc_em$SWELL)

lowswell <- filter(effort_marc_em, SWELL == "<2")
s_day <- hms(lowswell$VIS_DAY_OBS) %>% period_to_seconds()
s_day <- (((sum(s_day, na.rm=TRUE))/60)/60)
s_night <- hms(lowswell$VIS_NIGHT_OBS) %>% period_to_seconds()
s_night <- (((sum(s_night, na.rm=TRUE))/60)/60)
s_PAM <- hms(lowswell$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
s_PAM <- (((sum(s_PAM, na.rm=TRUE))/60)/60)
d_PAM <- hms(lowswell$VIS_PAM_DAY_OBS) %>% period_to_seconds()
d_PAM <- (((sum(d_PAM, na.rm=TRUE))/60)/60)
low_swell <- (s_day + s_night + s_PAM + d_PAM)
#swell 2-4 meters- 143.08 hrs
midswell <- filter(effort_marc_em, SWELL == "2-4")
m_day <- hms(midswell$VIS_DAY_OBS) %>% period_to_seconds()
m_day <- (((sum(m_day, na.rm=TRUE))/60)/60)
m_night <- hms(midswell$VIS_NIGHT_OBS) %>% period_to_seconds()
m_night <- (((sum(m_night, na.rm=TRUE))/60)/60)
m_PAM <- hms(midswell$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
m_PAM <- (((sum(m_PAM, na.rm=TRUE))/60)/60)
mid_swell <- (m_day + m_night + m_PAM)

Swell = c("Less than 2 m", "2 to 4 m")
Duration <- c(low_swell, mid_swell)%>% round(digits=2)
df<- data.frame(Swell=Swell, Duration=Duration)
  
Swell_table <- gt(df) %>% cols_label(Swell = "Swell", Duration= "Duration (HH.HH)")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
Swell_table
```

Beaufort Sea State during monitoring:

```{r}
#| echo: false
#| warning: false

#Beaufort Sea State during monitoring
#B0
effort_B0 <- filter(effort_marc_em, BEAUF == 0)
effort_B0_day <- hms(effort_B0$VIS_DAY_OBS) %>% period_to_seconds()
effort_B0_day <- (((sum(effort_B0_day, na.rm=TRUE))/60)/60)
effort_B0_night <- hms(effort_B0$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B0_night <- (((sum(effort_B0_night, na.rm=TRUE))/60)/60)
effort_B0_PAM <- hms(effort_B0$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B0_PAM <- (((sum(effort_B0_PAM, na.rm=TRUE))/60)/60)
effort_B0_P <- hms(effort_B0$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_B0_P <- (((sum(effort_B0_P, na.rm=TRUE))/60)/60)
b0 <- (effort_B0_day + effort_B0_night + effort_B0_PAM + effort_B0_P)
#B1 
effort_B1 <- filter(effort_marc_em, BEAUF == 1)
effort_B1_day <- hms(effort_B1$VIS_DAY_OBS) %>% period_to_seconds()
effort_B1_day <- (((sum(effort_B1_day, na.rm=TRUE))/60)/60)
effort_B1_night <- hms(effort_B1$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B1_night <- (((sum(effort_B1_night, na.rm=TRUE))/60)/60)
effort_B1_PAM <- hms(effort_B1$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B1_PAM <- (((sum(effort_B1_PAM, na.rm=TRUE))/60)/60)
effort_B1_P <- hms(effort_B1$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_B1_P <- (((sum(effort_B1_P, na.rm=TRUE))/60)/60)
b1 <- (effort_B1_day + effort_B1_night + effort_B1_PAM + effort_B1_P)
#B2
effort_B2 <- filter(effort_marc_em, BEAUF == 2)
effort_B2_day <- hms(effort_B2$VIS_DAY_OBS) %>% period_to_seconds()
effort_B2_day <- (((sum(effort_B2_day, na.rm=TRUE))/60)/60)
effort_B2_night <- hms(effort_B2$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B2_night <- (((sum(effort_B2_night, na.rm=TRUE))/60)/60)
effort_B2_PAM <- hms(effort_B2$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B2_PAM <- (((sum(effort_B2_PAM, na.rm=TRUE))/60)/60)
effort_B2_P <- hms(effort_B2$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_B2_P <- (((sum(effort_B2_P, na.rm=TRUE))/60)/60)
b2 <- (effort_B2_day + effort_B2_night + effort_B2_PAM +effort_B2_P)
#B3
effort_B3 <- filter(effort_marc_em, BEAUF == 3)
effort_B3_day <- hms(effort_B3$VIS_DAY_OBS) %>% period_to_seconds()
effort_B3_day <- (((sum(effort_B3_day, na.rm=TRUE))/60)/60)
effort_B3_night <- hms(effort_B3$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B3_night <- (((sum(effort_B3_night, na.rm=TRUE))/60)/60)
effort_B3_PAM <- hms(effort_B3$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B3_PAM <- (((sum(effort_B3_PAM, na.rm=TRUE))/60)/60)
effort_B3_PAM_d <- hms(effort_B3$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_B3_PAM_d <- (((sum(effort_B3_PAM_d, na.rm=TRUE))/60)/60)
b3<-(effort_B3_day + effort_B3_night + effort_B3_PAM+effort_B3_PAM_d)
#B4
effort_B4 <- filter(effort_marc_em, BEAUF == 4)
effort_B4_day <- hms(effort_B4$VIS_DAY_OBS) %>% period_to_seconds()
effort_B4_day <- (((sum(effort_B4_day, na.rm=TRUE))/60)/60)
effort_B4_night <- hms(effort_B4$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B4_night <- (((sum(effort_B4_night, na.rm=TRUE))/60)/60)
effort_B4_PAM <- hms(effort_B4$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B4_PAM <- (((sum(effort_B4_PAM, na.rm=TRUE))/60)/60)
b4<-(effort_B4_day + effort_B4_night + effort_B4_PAM)
#B5
effort_B5 <- filter(effort_marc_em, BEAUF == 5)
effort_B5_day <- hms(effort_B5$VIS_DAY_OBS) %>% period_to_seconds()
effort_B5_day <- (((sum(effort_B5_day, na.rm=TRUE))/60)/60)
effort_B5_night <- hms(effort_B5$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B5_night <- (((sum(effort_B5_night, na.rm=TRUE))/60)/60)
effort_B5_PAM <- hms(effort_B5$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B5_PAM <- (((sum(effort_B5_PAM, na.rm=TRUE))/60)/60)
b5<-(effort_B5_day + effort_B5_night + effort_B5_PAM)
#B6
effort_B6 <- filter(effort_marc_em, BEAUF == 6)
effort_B6_day <- hms(effort_B6$VIS_DAY_OBS) %>% period_to_seconds()
effort_B6_day <- (((sum(effort_B6_day, na.rm=TRUE))/60)/60)
effort_B6_night <- hms(effort_B6$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B6_night <- (((sum(effort_B6_night, na.rm=TRUE))/60)/60)
effort_B6_PAM <- hms(effort_B6$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B6_PAM <- (((sum(effort_B6_PAM, na.rm=TRUE))/60)/60)
b6<-(effort_B6_day + effort_B6_night + effort_B6_PAM)

effort_B7 <- filter(effort_marc_em, BEAUF == 7)
effort_B7_day <- hms(effort_B7$VIS_DAY_OBS) %>% period_to_seconds()
effort_B7_day <- (((sum(effort_B7_day, na.rm=TRUE))/60)/60)
effort_B7_night <- hms(effort_B7$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B7_night <- (((sum(effort_B7_night, na.rm=TRUE))/60)/60)
effort_B7_PAM <- hms(effort_B7$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B7_PAM <- (((sum(effort_B7_PAM, na.rm=TRUE))/60)/60)
b7<-(effort_B7_day + effort_B7_night + effort_B7_PAM)

effort_B8 <- filter(effort_marc_em, BEAUF == 8)
effort_B8_day <- hms(effort_B8$VIS_DAY_OBS) %>% period_to_seconds()
effort_B8_day <- (((sum(effort_B8_day, na.rm=TRUE))/60)/60)
effort_B8_night <- hms(effort_B8$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B8_night <- (((sum(effort_B8_night, na.rm=TRUE))/60)/60)
effort_B8_PAM <- hms(effort_B8$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B8_PAM <- (((sum(effort_B8_PAM, na.rm=TRUE))/60)/60)
b8<-(effort_B8_day + effort_B8_night + effort_B8_PAM)
total <- b0+b1+b2+b3+b4+b5+b6+b7+b8

Beaufort = c("B0", "B1", "B2", "B3", "B4", "B5", "B6", "B7", "B8", "Total")
Duration <- c(b0, b1, b2, b3, b4, b5, b6, b7, b8, total)%>% round(digits=2)
df<- data.frame(Beaufort=Beaufort, Duration=Duration)
  
Beauf_table <- gt(df) %>% cols_label(Beaufort = "Beaufort Sea State", Duration= "Duration (HH.HH)")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
Beauf_table
```

### Visual Detections

Total number of detection events by species:

\[SOME OF THESE NUMBERS ARE DIFFERENT THAN WHAT WAS REPORTED\]

```{r}
#| echo: false
#| warning: false
visualdetect_marc_em <- visualdetect %>% filter(VESSEL == "Emma McCall" & PROJECT_NUMBER == 222794 | VESSEL == "Marcelle Bordelon" & PROJECT_NUMBER == 219236)

individuals_summary <- visualdetect_marc_em %>%
  group_by(NAME_COMMON) %>%
  summarize(
    total_value = sum(TOT_NUM),
            average_value = round(mean(TOT_NUM),1),
            dist_value = round(mean(RANGE_VESSEL_START),0))

ind_table <- gt(individuals_summary) %>% cols_label(NAME_COMMON = "Species",
                  total_value = "Individuals Count",
                  average_value = "Average group size",
                  dist_value = "Average distance (m) at first detection")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )

ind_table
```

Closest point of approach (CPA) to source:

```{r}
#| echo: false
#| warning: false

visualdetect_marc_em$MITZONE_SILENTSOURCE_DIST <- as.numeric(visualdetect_marc_em$MITZONE_SILENTSOURCE_DIST)

CPA <- visualdetect_marc_em %>%
  group_by(NAME_COMMON) %>%
  summarize(active_value = round(mean(MITZONE_ACTIVESOURCE_DIST, na.rm = TRUE),2),
            inactive_value = round(mean(MITZONE_SILENTSOURCE_DIST, na.rm = TRUE),2))


CPA_table <- gt(CPA) %>% cols_label(NAME_COMMON = "Species",
                  active_value = "Mean CPA to active sparker (meters)",
                  inactive_value = "Mean CPA to silent sparker (meters)") %>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )

CPA_table
```

### Incidental Harassment Authorization (IHA) Level B Exposures

```{r}
#| echo: false 
#| warning: false  
 
take <- visualdetect_marc_em %>% group_by(NAME_COMMON) %>%   
  summarize(take_value = sum(LEVELB_TAKE, na.rm = TRUE))   

take_table <- gt(take) %>% cols_label(NAME_COMMON = "Species", take_value = "Total Number of Animals Observed Inside the Level B Harassment Zone") %>%  tab_options(     data_row.padding = px(1),     table.align = "left"   )  

take_table
```

### Acoustic Detections

Acoustic detections during survey:

```{r}
#| echo: false
#| warning: false

acousdetect_marc_em <- acousticdetect %>% filter(VESSEL == "Emma McCall" & PROJECT_NUMBER == 222794 | VESSEL == "Marcelle Bordelon" & PROJECT_NUMBER == 219236)
acousdetect_marc_em$NAME_COMMON <- gsub("Unidentifiable Dolphin", "Unidentifiable dolphin", acousdetect_marc_em$NAME_COMMON )
acousdetect_marc_em$MITZONE_SILENTSOURCE_DIST <- as.numeric(acousdetect_marc_em$MITZONE_SILENTSOURCE_DIST )

acousdetections <- acousdetect_marc_em%>%
  group_by(NAME_COMMON) %>%
  summarize(active_value = round(mean(MITZONE_ACTIVESOURCE_DIST, na.rm = TRUE),2),
            inactive_value = round(mean(MITZONE_SILENTSOURCE_DIST, na.rm = TRUE),2), total_value = sum(ANIMAL_BEST))



acoustic_table <- gt(acousdetections) %>% cols_label(NAME_COMMON = "Species",
active_value = "CPA when sparker was active", inactive_value = "CPA when sparker was inactive", total_value = "Estimated total number of individuals detected") %>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )

acoustic_table
```

### Port Calls

Port calls during the survey:

```{r}
#| echo: false
#| warning: false

portcall_em_marc <- portcall %>% filter(VESSEL == "Emma McCall" & PROJECT_NUMBER == 222794 | VESSEL == "Marcelle Bordelon" & PROJECT_NUMBER == 219236)


portcall_table <- gt(portcall_em_marc)%>% cols_label(PROJECT_NUMBER = "Project Number", VESSEL = "Vessel", DATE = "Date", TIME = "Time", PORT = "Port", ACTION = "Action", COMMENT_PORT_CALL= "Comments") %>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )

portcall_table
```
