---
title: "Bluepoint Wind"
format: html
editor: visual
css: styles.css
editor_options: 
  chunk_output_type: console
---

## Results

### Operation Activity

Total hours of regulated source operation:

\[HOURS OF SOURCE OPERATION FROM TIME AND TIDE DIFFERENT THAN WHAT IS REPORTED, TOTAL HOURS OF SOURCE OPERATION DIFFERENT THAN WHAT IS REPORTED\]

```{r}
#| echo: false
#| warning: false

#load libraries
library(readr)
library(tidyverse)
library(dplyr)
library(tidyr)
library(stringr)
library(gt)

#import tidy data
visualdetect <- readr::read_csv("data/2023/Bluepoint/Bluepoint_VisualDetect_Tidy.csv", locale = locale(encoding = "latin1"))
effort <- readr::read_csv("data/2023/Bluepoint/Bluepoint_Effort_Tidy.csv", locale = locale(encoding = "latin1"))
operations <- readr::read_csv("data/2023/Bluepoint/Bluepoint_Operations_Tidy.csv", locale = locale(encoding = "latin1"))
#portcall <- readr::read_csv("data/COSW/COSW_PortCall_Tidy.csv", locale = locale(encoding = "latin1"))
project <- readr::read_csv("data/2023/Bluepoint/Bluepoint_Project_Tidy.csv", locale = locale(encoding = "latin1"))
#Go Adventurer
operations_adventurer <- operations %>% filter(VESSEL == "Go Adventurer") 

sparker_sursource <- operations_adventurer %>% hms(operations_adventurer$DUR_SURSOURCE) %>% period_to_seconds()
sparker_sursource <- (((sum(sparker_sursource, na.rm=TRUE))/60)/60)

sparker_soft <- operations_adventurer %>% hms(operations_adventurer$DUR_SOFTSTART) %>% period_to_seconds()
sparker_soft <- (((sum(sparker_soft, na.rm=TRUE))/60)/60)

sparker_test <- operations_adventurer %>% hms(operations_adventurer$DUR_TEST) %>% period_to_seconds()
sparker_test <- (((sum(sparker_test, na.rm=TRUE))/60)/60)

sparker_presursource <- operations_adventurer %>% hms(operations_adventurer$DUR_PRESURSOURCE) %>% period_to_seconds()
sparker_presursource <- (((sum(sparker_presursource, na.rm=TRUE))/60)/60)

sparker_postsur <- operations_adventurer %>% hms(operations_adventurer$DUR_POSTSUR) %>% period_to_seconds()
sparker_postsur <- (((sum(sparker_postsur, na.rm=TRUE))/60)/60)

total_sparkerop_adventurer <- sum(sparker_sursource, sparker_soft, sparker_test, sparker_presursource, sparker_postsur)
#Time and Tide
operations_timetide <- operations %>% filter(VESSEL == "Time and Tide") 

sparker_sursource <- operations_timetide %>% hms(operations_timetide$DUR_SURSOURCE) %>% period_to_seconds()
sparker_sursource <- (((sum(sparker_sursource, na.rm=TRUE))/60)/60)

sparker_soft <- operations_timetide %>% hms(operations_timetide$DUR_SOFTSTART) %>% period_to_seconds()
sparker_soft <- (((sum(sparker_soft, na.rm=TRUE))/60)/60)

sparker_test <- operations_timetide %>% hms(operations_timetide$DUR_TEST) %>% period_to_seconds()
sparker_test <- (((sum(sparker_test, na.rm=TRUE))/60)/60)

sparker_presursource <- operations_timetide %>% hms(operations_timetide$DUR_PRESURSOURCE) %>% period_to_seconds()
sparker_presursource <- (((sum(sparker_presursource, na.rm=TRUE))/60)/60)

sparker_postsur <- operations_timetide %>% hms(operations_timetide$DUR_POSTSUR) %>% period_to_seconds()
sparker_postsur <- (((sum(sparker_postsur, na.rm=TRUE))/60)/60)

total_sparkerop_timetide <- sum(sparker_sursource, sparker_soft, sparker_test, sparker_presursource, sparker_postsur)
#Gerry Bordelon
operations_gerry <- operations %>% filter(VESSEL == "Gerry Bordelon") 

sparker_sursource <- operations_gerry %>% hms(operations_gerry$DUR_SURSOURCE) %>% period_to_seconds()
sparker_sursource <- (((sum(sparker_sursource, na.rm=TRUE))/60)/60)

sparker_soft <- operations_gerry %>% hms(operations_gerry$DUR_SOFTSTART) %>% period_to_seconds()
sparker_soft <- (((sum(sparker_soft, na.rm=TRUE))/60)/60)

sparker_test <- operations_gerry%>% hms(operations_gerry$DUR_TEST) %>% period_to_seconds()
sparker_test <- (((sum(sparker_test, na.rm=TRUE))/60)/60)

sparker_presursource <- operations_gerry %>% hms(operations_gerry$DUR_PRESURSOURCE) %>% period_to_seconds()
sparker_presursource <- (((sum(sparker_presursource, na.rm=TRUE))/60)/60)

sparker_postsur <- operations_gerry %>% hms(operations_gerry$DUR_POSTSUR) %>% period_to_seconds()
sparker_postsur <- (((sum(sparker_postsur, na.rm=TRUE))/60)/60)

total_sparkerop_gerry <- sum(sparker_sursource, sparker_soft, sparker_test, sparker_presursource, sparker_postsur)
#Henry Hudson
operations_henry <- operations %>% filter(VESSEL == "Henry Hudson") 

sparker_sursource <- operations_henry %>% hms(operations_henry$DUR_SURSOURCE) %>% period_to_seconds()
sparker_sursource <- (((sum(sparker_sursource, na.rm=TRUE))/60)/60)

sparker_soft <- operations_henry%>% hms(operations_henry$DUR_SOFTSTART) %>% period_to_seconds()
sparker_soft <- (((sum(sparker_soft, na.rm=TRUE))/60)/60)

sparker_test <- operations_henry%>% hms(operations_henry$DUR_TEST) %>% period_to_seconds()
sparker_test <- (((sum(sparker_test, na.rm=TRUE))/60)/60)

sparker_presursource <- operations_henry %>% hms(operations_henry$DUR_PRESURSOURCE) %>% period_to_seconds()
sparker_presursource <- (((sum(sparker_presursource, na.rm=TRUE))/60)/60)

sparker_postsur <- operations_henry %>% hms(operations_henry$DUR_POSTSUR) %>% period_to_seconds()
sparker_postsur <- (((sum(sparker_postsur, na.rm=TRUE))/60)/60)

total_sparkerop_henry <- sum(sparker_sursource, sparker_soft, sparker_test, sparker_presursource, sparker_postsur)

ops_total <- total_sparkerop_adventurer+total_sparkerop_timetide+ total_sparkerop_gerry+total_sparkerop_henry 
vessel <- c("Go Adventurer", "Time and Tide", "Gerry Bordelon", "Henry Hudson", "Total")
date <- c("3/8/2023- 9/9/2023", "4/14/2023 - 10/31/2023", "4/21/2023 - 8/7/2023", "12/28/2023 - 2/7/2024" , "")
operation <- c(total_sparkerop_adventurer, total_sparkerop_timetide, total_sparkerop_gerry , total_sparkerop_henry, ops_total)%>% round(digits=2)
df <- data.frame(vessel = vessel, date=date, operation = operation)

op_table <- gt(df) %>% cols_label(vessel = "Survey Vessel", date= "Dates of PSO Monitored Operation", operation= "Total Hours of Source Operation (HH.HH)")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
op_table
```

### Monitoring Effort

Summary of monitoring effort:

\[MANY VALUES DIFFERENT THAN WHAT WAS REPORTED\]

```{r}
#| echo: false
#| warning: false

#adventurer
effort_adventurer <- effort %>% filter(VESSEL == "Go Adventurer") 
day_obs <- hms(effort_adventurer$VIS_DAY_OBS)
night_obs <- hms(effort_adventurer$VIS_NIGHT_OBS)
day_obs_sec <- period_to_seconds(day_obs)
adv_day_obs_hrs <- (((sum(day_obs_sec, na.rm=TRUE))/60)/60)
night_obs_sec <- period_to_seconds(night_obs)
adv_night_obs_hrs <- (((sum(night_obs_sec, na.rm=TRUE))/60)/60)
adv_total_obs_adventurer <- (adv_day_obs_hrs + adv_night_obs_hrs)
#sparkers active 
sparkers_day <- (hms(effort_adventurer$SOURCE_DAY_OBS))
sparkers_day_sec <- period_to_seconds(sparkers_day)
adv_sparkers_day_hrs <- (((sum(sparkers_day_sec, na.rm=TRUE))/60)/60)
sparkers_nite <- hms(effort_adventurer$SOURCE_NIGHT_OBS)
sparkers_nite_sec <- period_to_seconds(sparkers_nite)
adv_sparkers_nite_hrs <- (((sum(sparkers_nite_sec, na.rm=TRUE))/60)/60)
adv_sparkers_active <- adv_sparkers_day_hrs + adv_sparkers_nite_hrs
adv_sparkers_inactive <- adv_total_obs_adventurer - adv_sparkers_active

#Time and Tide
effort_time <- effort %>% filter(VESSEL == "Time and Tide") 
day_obs <- hms(effort_time $VIS_DAY_OBS)
night_obs <- hms(effort_time $VIS_NIGHT_OBS)
day_obs_sec <- period_to_seconds(day_obs)
time_day_obs_hrs <- (((sum(day_obs_sec, na.rm=TRUE))/60)/60)
night_obs_sec <- period_to_seconds(night_obs)
time_night_obs_hrs <- (((sum(night_obs_sec, na.rm=TRUE))/60)/60)
time_total_obs_time <- (time_day_obs_hrs + time_night_obs_hrs)
#sparkers active 
sparkers_day <- (hms(effort_time$SOURCE_DAY_OBS))
sparkers_day_sec <- period_to_seconds(sparkers_day)
time_sparkers_day_hrs <- (((sum(sparkers_day_sec, na.rm=TRUE))/60)/60)
sparkers_nite <- hms(effort_time$SOURCE_NIGHT_OBS)
sparkers_nite_sec <- period_to_seconds(sparkers_nite)
time_sparkers_nite_hrs <- (((sum(sparkers_nite_sec, na.rm=TRUE))/60)/60)
time_sparkers_active <- time_sparkers_day_hrs + time_sparkers_nite_hrs
#Gerry Bordelon
effort_gerry <- effort %>% filter(VESSEL == "Gerry Bordelon") 
day_obs <- hms(effort_gerry$VIS_DAY_OBS)
night_obs <- hms(effort_gerry$VIS_NIGHT_OBS)
day_obs_sec <- period_to_seconds(day_obs)
gerry_day_obs_hrs <- (((sum(day_obs_sec, na.rm=TRUE))/60)/60)
night_obs_sec <- period_to_seconds(night_obs)
gerry_night_obs_hrs <- (((sum(night_obs_sec, na.rm=TRUE))/60)/60)
gerry_total_obs_gerry <- (gerry_day_obs_hrs + gerry_night_obs_hrs)

#Henry Hudson
effort_henry <- effort %>% filter(VESSEL == "Henry Hudson") 
day_obs <- hms(effort_henry$VIS_DAY_OBS)
night_obs <- hms(effort_henry$VIS_NIGHT_OBS)
day_obs_sec <- period_to_seconds(day_obs)
henry_day_obs_hrs <- (((sum(day_obs_sec, na.rm=TRUE))/60)/60)
night_obs_sec <- period_to_seconds(night_obs)
henry_night_obs_hrs <- (((sum(night_obs_sec, na.rm=TRUE))/60)/60)
henry_total_obs_henry <- (henry_day_obs_hrs + henry_night_obs_hrs)
#sparkers active 
sparkers_day <- (hms(effort_henry$SOURCE_DAY_OBS))
sparkers_day_sec <- period_to_seconds(sparkers_day)
henry_sparkers_day_hrs <- (((sum(sparkers_day_sec, na.rm=TRUE))/60)/60)
sparkers_nite <- hms(effort_henry$SOURCE_NIGHT_OBS)
sparkers_nite_sec <- period_to_seconds(sparkers_nite)
henry_sparkers_nite_hrs <- (((sum(sparkers_nite_sec, na.rm=TRUE))/60)/60)
henry_sparkers_active <- henry_sparkers_day_hrs + henry_sparkers_nite_hrs

#Carta
effort_carta <- effort %>% filter(VESSEL == "Carta") 
day_obs <- hms(effort_carta$VIS_DAY_OBS)
night_obs <- hms(effort_carta$VIS_NIGHT_OBS)
day_obs_sec <- period_to_seconds(day_obs)
carta_day_obs_hrs <- (((sum(day_obs_sec, na.rm=TRUE))/60)/60)
night_obs_sec <- period_to_seconds(night_obs)
carta_night_obs_hrs <- (((sum(night_obs_sec, na.rm=TRUE))/60)/60)
carta_total_obs_carta <- (carta_day_obs_hrs + carta_night_obs_hrs)

#Brooks McCall
effort_brooks <- effort %>% filter(VESSEL == "Brooks McCall") 
day_obs <- hms(effort_brooks$VIS_DAY_OBS)
night_obs <- hms(effort_brooks$VIS_NIGHT_OBS)
day_obs_sec <- period_to_seconds(day_obs)
brooks_day_obs_hrs <- (((sum(day_obs_sec, na.rm=TRUE))/60)/60)
night_obs_sec <- period_to_seconds(night_obs)
brooks_night_obs_hrs <- (((sum(night_obs_sec, na.rm=TRUE))/60)/60)
brooks_total_obs_brooks <- (brooks_day_obs_hrs + brooks_night_obs_hrs)

#William M
effort_will <- effort %>% filter(VESSEL == "William M") 
day_obs <- hms(effort_will$VIS_DAY_OBS)
night_obs <- hms(effort_will$VIS_NIGHT_OBS)
day_obs_sec <- period_to_seconds(day_obs)
will_day_obs_hrs <- (((sum(day_obs_sec, na.rm=TRUE))/60)/60)
night_obs_sec <- period_to_seconds(night_obs)
will_night_obs_hrs <- (((sum(night_obs_sec, na.rm=TRUE))/60)/60)
will_total_obs_will <- (will_day_obs_hrs + will_night_obs_hrs)

#Explorer
effort_explore <- effort %>% filter(VESSEL == "Fugro Explorer") 
day_obs <- hms(effort_explore$VIS_DAY_OBS)
night_obs <- hms(effort_explore$VIS_NIGHT_OBS)
day_obs_sec <- period_to_seconds(day_obs)
explore_day_obs_hrs <- (((sum(day_obs_sec, na.rm=TRUE))/60)/60)
night_obs_sec <- period_to_seconds(night_obs)
explore_night_obs_hrs <- (((sum(night_obs_sec, na.rm=TRUE))/60)/60)
explore_total_obs_explore <- (explore_day_obs_hrs + explore_night_obs_hrs)

#Tidewater Regulus
effort_tide <- effort %>% filter(VESSEL == "Tidewater Regulus") 
day_obs <- hms(effort_tide$VIS_DAY_OBS)
night_obs <- hms(effort_tide$VIS_NIGHT_OBS)
day_obs_sec <- period_to_seconds(day_obs)
regal_day_obs_hrs <- (((sum(day_obs_sec, na.rm=TRUE))/60)/60)
night_obs_sec <- period_to_seconds(night_obs)
regal_night_obs_hrs <- (((sum(night_obs_sec, na.rm=TRUE))/60)/60)
regal_total_obs_tide <- (regal_day_obs_hrs + regal_night_obs_hrs)

monitoring <- c("Source active", "Source not active", "Daytime", "Nighttime", "Total")
go_adventurer <- c(adv_sparkers_active, adv_sparkers_inactive, adv_day_obs_hrs, adv_night_obs_hrs, adv_total_obs_adventurer) %>% round(digits=2)
time_tide <- c(time_sparkers_active, 0, time_day_obs_hrs, time_night_obs_hrs, time_total_obs_time)%>% round(digits=2)
gerry_b <- c(0, 0, gerry_day_obs_hrs, gerry_night_obs_hrs, gerry_total_obs_gerry)%>% round(digits=2)
henry_h <- c(henry_sparkers_active, (henry_total_obs_henry - henry_sparkers_active), henry_day_obs_hrs, henry_night_obs_hrs, henry_total_obs_henry)%>% round(digits=2)
regulus <- c(0, 0, regal_day_obs_hrs, regal_night_obs_hrs, regal_total_obs_tide)%>% round(digits=2)
explorer  <- c(0, 0, explore_day_obs_hrs, explore_night_obs_hrs, explore_total_obs_explore)%>% round(digits=2)
carta<- c(0, 0, carta_day_obs_hrs, carta_night_obs_hrs, carta_total_obs_carta)%>% round(digits=2)
brooks<- c(0, 0, brooks_day_obs_hrs, brooks_night_obs_hrs, brooks_total_obs_brooks)%>% round(digits=2)
william<- c(0, 0, will_day_obs_hrs, will_night_obs_hrs, will_total_obs_will)%>% round(digits=2)

df <- data.frame(Monitoring=monitoring, Go_Adventurer = go_adventurer, Time=time_tide, Gerry=gerry_b, Henry=henry_h, Regulus=regulus, Explorer=explorer, Carta=carta, Brooks=brooks, William=william)

monitoring_table <- gt(df) %>% cols_label(Monitoring = "Monitoring Effort by Source Activity", Go_Adventurer= "M/V Go Adventurer", Time = "M/V Time and Tide", Gerry = "M/V Gerry Bordelon", Henry="M/V Henry Hudson", Regulus = "M/V Regulus", Explorer = "M/V Explorer", Carta= "M/V Carta", Brooks="M/V Brooks McCall", William = "M/V William M")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
monitoring_table
```

### Environmental Conditions

Summary of visibility conditions during the survey:

\[DIFFERENT THAN WHAT WAS REPORTED\]

```{r}
#| echo: false
#| warning: false

#visibility conditions
#monitoring effort with >5 km visibiilIty 
effort_highvis <- filter(effort, VISIBIL == ">5" | VISIBIL == "6" | VISIBIL == "7" | VISIBIL == "8" |VISIBIL == "9" | VISIBIL == "10")
effort_high <- hms(effort_highvis$VIS_DAY_OBS) %>% period_to_seconds()
effort_high <- (((sum(effort_high, na.rm=TRUE))/60)/60)
effort_s <- hms(effort_highvis$SOURCE_DAY_OBS) %>% period_to_seconds()
effort_s <- (((sum(effort_s, na.rm=TRUE))/60)/60)
effort_n <- hms(effort_highvis$SOURCE_NIGHT_OBS) %>% period_to_seconds()
effort_n <- (((sum(effort_n, na.rm=TRUE))/60)/60)
effort_high_PV <- hms(effort_highvis$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_high_PV <- (((sum(effort_high_PV, na.rm=TRUE))/60)/60)
effort_night <- hms(effort_highvis$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_night <- (((sum(effort_night, na.rm=TRUE))/60)/60)
effort_high_P <- hms(effort_highvis$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_high_P <- (((sum(effort_high_P, na.rm=TRUE))/60)/60)
greater_five <- (effort_high + effort_high_PV + effort_night + effort_high_P + effort_s + effort_n)

effort_midvis <- filter(effort, VISIBIL == "2-5" | VISIBIL == "2" | VISIBIL == "3" | VISIBIL == "4" | VISIBIL == "5" )
effort_midvis_day <- hms(effort_midvis$VIS_DAY_OBS) %>% period_to_seconds()
effort_midvis_day <- (((sum(effort_midvis_day, na.rm=TRUE))/60)/60)
effort_mid_s <- hms(effort_midvis$SOURCE_DAY_OBS) %>% period_to_seconds()
effort_mid_s <- (((sum(effort_s, na.rm=TRUE))/60)/60)
effort_mid_n <- hms(effort_midvis$SOURCE_NIGHT_OBS) %>% period_to_seconds()
effort_mid_n <- (((sum(effort_n, na.rm=TRUE))/60)/60)
effort_midvis_night <- hms(effort_midvis$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_midvis_night <- (((sum(effort_midvis_night, na.rm=TRUE))/60)/60)
effort_midvis_PV <- hms(effort_midvis$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_midvis_PV <- (((sum(effort_midvis_PV, na.rm=TRUE))/60)/60)
effort_midvis_P <- hms(effort_midvis$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_midvis_P <- (((sum(effort_midvis_P, na.rm=TRUE))/60)/60)

two_to_five <- (effort_midvis_day + effort_midvis_night + effort_midvis_P + effort_midvis_PV + effort_mid_s + effort_mid_n)

effort_lowvis <- filter(effort, VISIBIL == "0.5-1" | VISIBIL == "1-2" | VISIBIL == "0.05-0.1" |VISIBIL == "0.3-0.5" | VISIBIL == "<.05" |VISIBIL == "0.1-0.3" | VISIBIL == "1" | VISIBIL == "0.5" | VISIBIL == "0.6" |VISIBIL == "0.7" | VISIBIL == "0.8" |VISIBIL == "0.9" |VISIBIL == "0.2" |VISIBIL == "0.3" | VISIBIL == "0.4" )
effort_lowvis_day <- hms(effort_lowvis$VIS_DAY_OBS) %>% period_to_seconds()
effort_lowvis_day <- (((sum(effort_lowvis_day, na.rm=TRUE))/60)/60)
effort_lowvis_night <- hms(effort_lowvis$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_lowvis_night <- (((sum(effort_lowvis_night, na.rm=TRUE))/60)/60)
effort_low_s <- hms(effort_lowvis$SOURCE_DAY_OBS) %>% period_to_seconds()
effort_low_s <- (((sum(effort_s, na.rm=TRUE))/60)/60)
effort_low_n <- hms(effort_lowvis$SOURCE_NIGHT_OBS) %>% period_to_seconds()
effort_low_n <- (((sum(effort_n, na.rm=TRUE))/60)/60)
effort_lowvis_PV <- hms(effort_lowvis$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_lowvis_PV <- (((sum(effort_lowvis_PV, na.rm=TRUE))/60)/60)
effort_lowvis_P <- hms(effort_lowvis$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_lowvis_P <- (((sum(effort_lowvis_P, na.rm=TRUE))/60)/60)
less_than_2 <- (effort_lowvis_P + effort_lowvis_PV + effort_lowvis_night + effort_lowvis_day+effort_low_n + effort_low_s)

Visibility <- c("Greater than 5 km", "2 to 5 km", "Less than 2 km")
Duration <- c(greater_five, two_to_five, less_than_2) %>% round(digits=2)
df<- data.frame(Visibility=Visibility, Duration=Duration)
  
visibility_table <- gt(df) %>% cols_label(Visibility = "Visibility", Duration= "Duration (HH.HH)")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
visibility_table
```

Beaufort Sea State during the survey:

\[DIFFERENT THAN WHAT WAS REPORTED\]

```{r}
#| echo: false
#| warning: false
#effort <- effort %>% mutate(VIS_DAY_OBS = ifelse(VESSEL=="Time and Tide", END_TIME- START_TIME, VIS_DAY_OBS))
#Beaufort Sea State during monitoring
#B0
effort_B0 <- filter(effort, BEAUF == 0)
effort_B0_day <- hms(effort_B0$VIS_DAY_OBS) %>% period_to_seconds()
effort_B0_day <- (((sum(effort_B0_day, na.rm=TRUE))/60)/60)
effort_B0_night <- hms(effort_B0$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B0_night <- (((sum(effort_B0_night, na.rm=TRUE))/60)/60)
effort_B0_PAM <- hms(effort_B0$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B0_PAM <- (((sum(effort_B0_PAM, na.rm=TRUE))/60)/60)
effort_B0_P <- hms(effort_B0$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_B0_P <- (((sum(effort_B0_P, na.rm=TRUE))/60)/60)
b0 <- (effort_B0_day + effort_B0_night + effort_B0_PAM + effort_B0_P)
#B1 
effort_B1 <- filter(effort, BEAUF == 1)
effort_B1_day <- hms(effort_B1$VIS_DAY_OBS) %>% period_to_seconds()
effort_B1_day <- (((sum(effort_B1_day, na.rm=TRUE))/60)/60)
effort_B1_night <- hms(effort_B1$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B1_night <- (((sum(effort_B1_night, na.rm=TRUE))/60)/60)
effort_B1_PAM <- hms(effort_B1$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B1_PAM <- (((sum(effort_B1_PAM, na.rm=TRUE))/60)/60)
effort_B1_P <- hms(effort_B1$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_B1_P <- (((sum(effort_B1_P, na.rm=TRUE))/60)/60)
b1 <- (effort_B1_day + effort_B1_night + effort_B1_PAM + effort_B1_P)
#B2
effort_B2 <- filter(effort, BEAUF == 2)
effort_B2_day <- hms(effort_B2$VIS_DAY_OBS) %>% period_to_seconds()
effort_B2_day <- (((sum(effort_B2_day, na.rm=TRUE))/60)/60)
effort_B2_night <- hms(effort_B2$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B2_night <- (((sum(effort_B2_night, na.rm=TRUE))/60)/60)
effort_B2_PAM <- hms(effort_B2$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B2_PAM <- (((sum(effort_B2_PAM, na.rm=TRUE))/60)/60)
effort_B2_P <- hms(effort_B2$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_B2_P <- (((sum(effort_B2_P, na.rm=TRUE))/60)/60)
b2 <- (effort_B2_day + effort_B2_night + effort_B2_PAM +effort_B2_P)
#B3
effort_B3 <- filter(effort, BEAUF == 3)
effort_B3_day <- hms(effort_B3$VIS_DAY_OBS) %>% period_to_seconds()
effort_B3_day <- (((sum(effort_B3_day, na.rm=TRUE))/60)/60)
effort_B3_night <- hms(effort_B3$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B3_night <- (((sum(effort_B3_night, na.rm=TRUE))/60)/60)
effort_B3_PAM <- hms(effort_B3$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B3_PAM <- (((sum(effort_B3_PAM, na.rm=TRUE))/60)/60)
effort_B3_PAM_d <- hms(effort_B3$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_B3_PAM_d <- (((sum(effort_B3_PAM_d, na.rm=TRUE))/60)/60)
b3<-(effort_B3_day + effort_B3_night + effort_B3_PAM+effort_B3_PAM_d)
#B4
effort_B4 <- filter(effort, BEAUF == 4)
effort_B4_day <- hms(effort_B4$VIS_DAY_OBS) %>% period_to_seconds()
effort_B4_day <- (((sum(effort_B4_day, na.rm=TRUE))/60)/60)
effort_B4_night <- hms(effort_B4$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B4_night <- (((sum(effort_B4_night, na.rm=TRUE))/60)/60)
effort_B4_PAM <- hms(effort_B4$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B4_PAM <- (((sum(effort_B4_PAM, na.rm=TRUE))/60)/60)
b4<-(effort_B4_day + effort_B4_night + effort_B4_PAM)
#B5
effort_B5 <- filter(effort, BEAUF == 5)
effort_B5_day <- hms(effort_B5$VIS_DAY_OBS) %>% period_to_seconds()
effort_B5_day <- (((sum(effort_B5_day, na.rm=TRUE))/60)/60)
effort_B5_night <- hms(effort_B5$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B5_night <- (((sum(effort_B5_night, na.rm=TRUE))/60)/60)
effort_B5_PAM <- hms(effort_B5$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B5_PAM <- (((sum(effort_B5_PAM, na.rm=TRUE))/60)/60)
b5<-(effort_B5_day + effort_B5_night + effort_B5_PAM)
#B6
effort_B6 <- filter(effort, BEAUF == 6)
effort_B6_day <- hms(effort_B6$VIS_DAY_OBS) %>% period_to_seconds()
effort_B6_day <- (((sum(effort_B6_day, na.rm=TRUE))/60)/60)
effort_B6_night <- hms(effort_B6$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B6_night <- (((sum(effort_B6_night, na.rm=TRUE))/60)/60)
effort_B6_PAM <- hms(effort_B6$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B6_PAM <- (((sum(effort_B6_PAM, na.rm=TRUE))/60)/60)
b6<-(effort_B6_day + effort_B6_night + effort_B6_PAM)
#B7
effort_B7 <- filter(effort, BEAUF == 7)
effort_B7_day <- hms(effort_B7$VIS_DAY_OBS) %>% period_to_seconds()
effort_B7_day <- (((sum(effort_B7_day, na.rm=TRUE))/60)/60)
effort_B7_night <- hms(effort_B7$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B7_night <- (((sum(effort_B7_night, na.rm=TRUE))/60)/60)
effort_B7_PAM <- hms(effort_B7$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B7_PAM <- (((sum(effort_B7_PAM, na.rm=TRUE))/60)/60)
b7<-(effort_B7_day + effort_B7_night + effort_B7_PAM)
#B8
effort_B8 <- filter(effort, BEAUF == 8)
effort_B8_day <- hms(effort_B8$VIS_DAY_OBS) %>% period_to_seconds()
effort_B8_day <- (((sum(effort_B8_day, na.rm=TRUE))/60)/60)
effort_B8_night <- hms(effort_B8$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B8_night <- (((sum(effort_B8_night, na.rm=TRUE))/60)/60)
effort_B8_PAM <- hms(effort_B8$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B8_PAM <- (((sum(effort_B8_PAM, na.rm=TRUE))/60)/60)
b8<-(effort_B8_day + effort_B8_night + effort_B8_PAM)
#B9
effort_B9 <- filter(effort, BEAUF == 9)
effort_B9_day <- hms(effort_B9$VIS_DAY_OBS) %>% period_to_seconds()
effort_B9_day <- (((sum(effort_B9_day, na.rm=TRUE))/60)/60)
effort_B9_night <- hms(effort_B9$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B9_night <- (((sum(effort_B9_night, na.rm=TRUE))/60)/60)
effort_B9_PAM <- hms(effort_B9$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B9_PAM <- (((sum(effort_B9_PAM, na.rm=TRUE))/60)/60)
b9<-(effort_B9_day + effort_B9_night + effort_B9_PAM)

total <- b0+b1+ b2+b3+b4+b5+b6+b7+b8+b9
Beaufort = c("B0", "B1", "B2", "B3", "B4","B5","B6","B7","B8","B9", "Total")
Duration <- c(b0, b1, b2, b3, b4,b5,b6,b7,b8,b9, total)%>% round(digits=2)
df<- data.frame(Beaufort=Beaufort, Duration=Duration)
  
Beauf_table <- gt(df) %>% cols_label(Beaufort = "Beaufort Sea State", Duration= "Duration (HH.HH)")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
Beauf_table
```

Swell height during monitoring during the survey:

\[DIFFERENT THAN WHAT WAS REPORTED\]

```{r}
#| echo: false
#| warning: false

lowswell <- filter(effort, SWELL == "<2" | SWELL == "0.4"| SWELL ==  "0.3" | SWELL == "0.5" | SWELL =="0.8" | SWELL =="1"| SWELL =="0.6"| SWELL =="0.7"| SWELL == "1.1" | SWELL =="0.9" | SWELL == "1.2" |SWELL == "1.3" | SWELL == "0.2"| SWELL ==  "0.6."|SWELL ==  "0.1" |SWELL ==  "1.5"|SWELL ==  "1.75"|SWELL == "0"|SWELL =="0.75")
s_day <- hms(lowswell$VIS_DAY_OBS) %>% period_to_seconds()
s_day <- (((sum(s_day, na.rm=TRUE))/60)/60)
s_night <- hms(lowswell$VIS_NIGHT_OBS) %>% period_to_seconds()
s_night <- (((sum(s_night, na.rm=TRUE))/60)/60)
s_PAM <- hms(lowswell$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
s_PAM <- (((sum(s_PAM, na.rm=TRUE))/60)/60)
d_PAM <- hms(lowswell$VIS_PAM_DAY_OBS) %>% period_to_seconds()
d_PAM <- (((sum(d_PAM, na.rm=TRUE))/60)/60)
low_swell <- (s_day + s_night + s_PAM + d_PAM)

midswell <- filter(effort, SWELL == "2-4")
m_day <- hms(midswell$VIS_DAY_OBS) %>% period_to_seconds()
m_day <- (((sum(m_day, na.rm=TRUE))/60)/60)
m_night <- hms(midswell$VIS_NIGHT_OBS) %>% period_to_seconds()
m_night <- (((sum(m_night, na.rm=TRUE))/60)/60)
m_PAM <- hms(midswell$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
m_PAM <- (((sum(m_PAM, na.rm=TRUE))/60)/60)
mid_swell <- (m_day + m_night + m_PAM)

highswell <- filter(effort, SWELL == ">4")
h_day <- hms(highswell$VIS_DAY_OBS) %>% period_to_seconds()
h_day <- (((sum(h_day, na.rm=TRUE))/60)/60)
h_night <- hms(highswell$VIS_NIGHT_OBS) %>% period_to_seconds()
h_night <- (((sum(h_night, na.rm=TRUE))/60)/60)
h_PAM <- hms(highswell$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
h_PAM <- (((sum(h_PAM, na.rm=TRUE))/60)/60)
high_swell <- (h_day + h_night + h_PAM)

total <- low_swell+mid_swell+high_swell
Swell = c("Less than 2 m", "2 to 4 m", "Greater than 4 m", "Total")
Duration <- c(low_swell, mid_swell, high_swell, total)%>% round(digits=2)
df<- data.frame(Swell=Swell, Duration=Duration)
  
Swell_table <- gt(df) %>% cols_label(Swell = "Swell", Duration= "Duration (HH.HH)")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
Swell_table
```

### Visual Detections

Total number of detection events by species:

```{r}
#| echo: false
#| warning: false

#change spelling of words
visualdetect$NAME_COMMON <- gsub("Bottlenose dolphin", "Bottlenose Dolphin", visualdetect$NAME_COMMON)
visualdetect$NAME_COMMON <- gsub("common dolphin", "Common Dolphin", visualdetect$NAME_COMMON)
visualdetect$NAME_COMMON <- gsub("Common dolphin", "Common Dolphin", visualdetect$NAME_COMMON)
visualdetect$NAME_COMMON <- gsub("Common bottlenose dolphin", "Bottlenose Dolphin", visualdetect$NAME_COMMON)
visualdetect$NAME_COMMON <- gsub("Fin whale", "Fin Whale", visualdetect$NAME_COMMON)
visualdetect$NAME_COMMON <- gsub("Sei whale", "Sei Whale", visualdetect$NAME_COMMON)
visualdetect$NAME_COMMON <- gsub("Humpback whale", "Humpback Whale", visualdetect$NAME_COMMON)
visualdetect$NAME_COMMON <- gsub("Unidentified whale", "Unidentified Whale", visualdetect$NAME_COMMON)
visualdetect$NAME_COMMON <- gsub("Unidentifiable whale", "Unidentified Whale", visualdetect$NAME_COMMON)
visualdetect$NAME_COMMON <- gsub("Unidentifiable baleen whale", "Unidentified Whale", visualdetect$NAME_COMMON)
visualdetect$NAME_COMMON <- gsub("Unidentifiable Dolphin", "Unidentified Dolphin", visualdetect$NAME_COMMON)
visualdetect$NAME_COMMON <- gsub("Unidentifiable dolphin", "Unidentified Dolphin", visualdetect$NAME_COMMON)
visualdetect$NAME_COMMON <- gsub("Unidentified dolphin", "Unidentified Dolphin", visualdetect$NAME_COMMON)


#detections by species
species_summary <- visualdetect %>%
  count(NAME_COMMON)
species_table <- gt(species_summary) %>% cols_label(NAME_COMMON = "Species",
                                          n = "Number of detection records")%>% tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
species_table
```

Total detected individuals by species, and detection and distance summaries:

```{r}
#| echo: false
#| warning: false
visualdetect$RANGE_VESSEL_START <- as.numeric(visualdetect$RANGE_VESSEL_START)

individuals_summary <- visualdetect %>%
  group_by(NAME_COMMON) %>%
  summarize(
    total_value = sum(TOT_NUM),
            average_value = round(mean(TOT_NUM),1),
            dist_value = round(mean(RANGE_VESSEL_START, na.rm = TRUE),0))

ind_table <- gt(individuals_summary) %>% cols_label(NAME_COMMON = "Species",
                  total_value = "Individuals Count",
                  average_value = "Average group size",
                  dist_value = "Average distance (m) at first detection")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )

ind_table
```

Closest point of approach (CPA) to source (sparker) during detections:

\[MEAN CPA TO SILENT SOURCE FOR UNIDENTIFIED DOLPHIN, HUMPBACK WHALE, UNIDENTIFIED WHALE ; MEAN CPA TO ACTIVE SOURCE FOR HUMPBACK WHALE DIFFERENT THAN WHAT WAS REPORTED\]

```{r}
#| echo: false
#| warning: false

CPA <- visualdetect%>%
  group_by(NAME_COMMON) %>%
  summarize(active_value = round(mean(MITZONE_ACTIVESOURCE_DIST, na.rm = TRUE),2),
            inactive_value = round(mean(MITZONE_SILENTSOURCE_DIST, na.rm = TRUE),2))

CPA_table <- gt(CPA) %>% cols_label(NAME_COMMON = "Species",
                  active_value = "Mean CPA to active sparker (meters)",
                  inactive_value = "Mean CPA to silent sparker (meters)") %>%  tab_options(
    data_row.padding = px(1),
    table.align = "left")

CPA_table
```

### Incidental Harassment Authorization (IHA) Level B Exposures

```{r}
#| echo: false
#| warning: false

take <- visualdetect %>% group_by(NAME_COMMON) %>%   
  summarize(take_value = sum(LEVELB_TAKE, na.rm = TRUE))   

take_table <- gt(take) %>% cols_label(NAME_COMMON = "Species", take_value = "Total Number of Animals Observed Inside the Level B Harassment Zone") %>%  tab_options(     data_row.padding = px(1),     table.align = "left"   )  

take_table
```
