---
title: "Community Offshore Wind"
format: html
editor: visual
css: styles.css
editor_options: 
  chunk_output_type: console
---

## Project 222066 (*Westerly*)

### Operation Activity

Total hours of sparker operation:

```{r}
#| echo: false
#| warning: false

#load libraries
library(readr)
library(tidyverse)
library(dplyr)
library(tidyr)
library(stringr)
library(gt)

#import tidy data
#import with latin encoding because some PSO names have accents
visualdetect <- readr::read_csv("data/2023/COSW/COSW_VisualDetect_Tidy.csv", locale = locale(encoding = "latin1"))
effort <- readr::read_csv("data/2023/COSW/COSW_Effort_Tidy.csv", locale = locale(encoding = "latin1"))
operations <- readr::read_csv("data/2023/COSW/COSW_Operations_Tidy.csv", locale = locale(encoding = "latin1"))
portcall <- readr::read_csv("data/2023/COSW/COSW_PortCall_Tidy.csv", locale = locale(encoding = "latin1"))
operations_westerly <- operations %>% filter(VESSEL == "Westerly") 

sparker_sursource <- operations_westerly %>% hms(operations_westerly$DUR_SURSOURCE) %>% period_to_seconds()
sparker_sursource <- (((sum(sparker_sursource, na.rm=TRUE))/60)/60)

sparker_soft <- operations_westerly %>% hms(operations_westerly$DUR_SOFTSTART) %>% period_to_seconds()
sparker_soft <- (((sum(sparker_soft, na.rm=TRUE))/60)/60)

sparker_test <- operations_westerly %>% hms(operations_westerly$DUR_TEST) %>% period_to_seconds()
sparker_test <- (((sum(sparker_test, na.rm=TRUE))/60)/60)

sparker_presursource <- operations_westerly %>% hms(operations_westerly$DUR_PRESURSOURCE) %>% period_to_seconds()
sparker_presursource <- (((sum(sparker_presursource, na.rm=TRUE))/60)/60)

sparker_postsur <- operations_westerly %>% hms(operations_westerly$DUR_POSTSUR) %>% period_to_seconds()
sparker_postsur <- (((sum(sparker_postsur, na.rm=TRUE))/60)/60)

total_sparkerop <- sum(sparker_sursource, sparker_soft, sparker_test, sparker_presursource, sparker_postsur)

vessel <- c("Westerly")
date <- c("8/28/2023 - 9/28/2023")
operation <- c(total_sparkerop)%>% round(digits=2)
df <- data.frame(vessel = vessel, date=date, operation = operation)

op_table <- gt(df) %>% cols_label(vessel = "Survey Vessel", date= "Dates of Operation", operation= "Total Hours of Sparker Operation (HH.HH)")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
op_table
```

### Monitoring Effort

Summary of monitoring effort:

```{r}
#| echo: false
#| warning: false

effort_westerly <- effort %>% filter(VESSEL == "Westerly") 
day_obs <- hms(effort_westerly$VIS_DAY_OBS)
night_obs <- hms(effort_westerly$VIS_NIGHT_OBS)
#no acoustic observations
day_obs_sec <- period_to_seconds(day_obs)
day_obs_hrs <- (((sum(day_obs_sec, na.rm=TRUE))/60)/60)
night_obs_sec <- period_to_seconds(night_obs)
night_obs_hrs <- (((sum(night_obs_sec, na.rm=TRUE))/60)/60)

total_obs <- (day_obs_hrs + night_obs_hrs)
#sparkers active 

sparkers_day <- (hms(effort_westerly$SOURCE_DAY_OBS))
sparkers_day_sec <- period_to_seconds(sparkers_day)
sparkers_day_hrs <- (((sum(sparkers_day_sec, na.rm=TRUE))/60)/60)
sparkers_nite <- hms(effort_westerly$SOURCE_NIGHT_OBS)
sparkers_nite_sec <- period_to_seconds(sparkers_nite)
sparkers_nite_hrs <- (((sum(sparkers_nite_sec, na.rm=TRUE))/60)/60)

sparkers_active <- sum(sparkers_nite_hrs + sparkers_day_hrs)
sparkers_inactive <- total_obs -sparkers_active 

monitoring <- c("Sparker active", "Sparker not active", "Daytime", "Nighttime", "Total")
visual <- c(sparkers_active, sparkers_inactive, day_obs_hrs, night_obs_hrs,  total_obs) %>% round(digits=2)


df <- data.frame(Monitoring=monitoring, Visual = visual)

monitoring_table <- gt(df) %>% cols_label(Monitoring = "Monitoring effort", Visual= "Visual (HH.HH)")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
monitoring_table
```

### Environmental Conditions

Summary of visibility conditions during the survey:

```{r}
#| echo: false
#| warning: false

effort_westerly$VISIBIL <- gsub("5-Feb", "2-5", effort_westerly$VISIBIL)
effort_westerly$VISIBIL <- gsub("2-Jan", "1-2", effort_westerly$VISIBIL)
#visibility conditions
#print(unique(effort_westerly$VISIBIL))
#monitoring effort with >5 km visibiilIty = 2211.18 hrs
effort_highvis <- filter(effort_westerly, VISIBIL == ">5")
effort_high <- hms(effort_highvis$VIS_DAY_OBS) %>% period_to_seconds()
effort_high <- (((sum(effort_high, na.rm=TRUE))/60)/60)
effort_high_PV <- hms(effort_highvis$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_high_PV <- (((sum(effort_high_PV, na.rm=TRUE))/60)/60)
effort_night <- hms(effort_highvis$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_night <- (((sum(effort_night, na.rm=TRUE))/60)/60)
effort_high_P <- hms(effort_highvis$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_high_P <- (((sum(effort_high_P, na.rm=TRUE))/60)/60)
greater_five <- (effort_high + effort_high_PV + effort_night + effort_high_P)

effort_midvis <- filter(effort_westerly, VISIBIL == "2-5")
effort_midvis_day <- hms(effort_midvis$VIS_DAY_OBS) %>% period_to_seconds()
effort_midvis_day <- (((sum(effort_midvis_day, na.rm=TRUE))/60)/60)
effort_midvis_night <- hms(effort_midvis$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_midvis_night <- (((sum(effort_midvis_night, na.rm=TRUE))/60)/60)
effort_midvis_PV <- hms(effort_midvis$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_midvis_PV <- (((sum(effort_midvis_PV, na.rm=TRUE))/60)/60)
effort_midvis_P <- hms(effort_midvis$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_midvis_P <- (((sum(effort_midvis_P, na.rm=TRUE))/60)/60)

two_to_five <- (effort_midvis_day + effort_midvis_night + effort_midvis_P + effort_midvis_PV)

effort_lowvis <- filter(effort_westerly, VISIBIL == "0.5-1" | VISIBIL == "1-2" | VISIBIL == "0.05-0.1" |
                          VISIBIL == "0.3-0.5" | VISIBIL == "<.05" |VISIBIL == "0.1-0.3" )
effort_lowvis_day <- hms(effort_lowvis$VIS_DAY_OBS) %>% period_to_seconds()
effort_lowvis_day <- (((sum(effort_lowvis_day, na.rm=TRUE))/60)/60)
effort_lowvis_night <- hms(effort_lowvis$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_lowvis_night <- (((sum(effort_lowvis_night, na.rm=TRUE))/60)/60)
effort_lowvis_PV <- hms(effort_lowvis$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_lowvis_PV <- (((sum(effort_lowvis_PV, na.rm=TRUE))/60)/60)
effort_lowvis_P <- hms(effort_lowvis$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_lowvis_P <- (((sum(effort_lowvis_P, na.rm=TRUE))/60)/60)

less_than_2 <- (effort_lowvis_P + effort_lowvis_PV + effort_lowvis_night + effort_lowvis_day)

Visibility <- c("Greater than 5 km", "2 to 5 km", "Less than 2 km")
Duration <- c(greater_five, two_to_five, less_than_2) %>% round(digits=2)
df<- data.frame(Visibility=Visibility, Duration=Duration)
  
visibility_table <- gt(df) %>% cols_label(Visibility = "Visibility", Duration= "Duration (HH.HH)")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
visibility_table
```

Summary of swell height during the survey:

```{r}
#| echo: false
#| warning: false

effort_westerly$SWELL <- gsub("4-Feb", "2-4", effort_westerly$SWELL)
lowswell <- filter(effort_westerly, SWELL == "<2")
s_day <- hms(lowswell$VIS_DAY_OBS) %>% period_to_seconds()
s_day <- (((sum(s_day, na.rm=TRUE))/60)/60)
s_night <- hms(lowswell$VIS_NIGHT_OBS) %>% period_to_seconds()
s_night <- (((sum(s_night, na.rm=TRUE))/60)/60)
s_PAM <- hms(lowswell$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
s_PAM <- (((sum(s_PAM, na.rm=TRUE))/60)/60)
d_PAM <- hms(lowswell$VIS_PAM_DAY_OBS) %>% period_to_seconds()
d_PAM <- (((sum(d_PAM, na.rm=TRUE))/60)/60)
low_swell <- (s_day + s_night + s_PAM + d_PAM)
#swell 2-4 meters- 143.08 hrs
# midswell <- filter(effort_westerly, SWELL == "2-4")
# m_day <- hms(midswell$VIS_DAY_OBS) %>% period_to_seconds()
# m_day <- (((sum(m_day, na.rm=TRUE))/60)/60)
# m_night <- hms(midswell$VIS_NIGHT_OBS) %>% period_to_seconds()
# m_night <- (((sum(m_night, na.rm=TRUE))/60)/60)
# m_PAM <- hms(midswell$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
# m_PAM <- (((sum(m_PAM, na.rm=TRUE))/60)/60)
# mid_swell <- (m_day + m_night + m_PAM)

Swell = c("Less than 2 m", "2 to 4 m")
Duration <- c(low_swell, 0)%>% round(digits=2)
df<- data.frame(Swell=Swell, Duration=Duration)
  
Swell_table <- gt(df) %>% cols_label(Swell = "Swell", Duration= "Duration (HH.HH)")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
Swell_table
```

Beaufort Sea State during the survey:

```{r}
#| echo: false
#| warning: false

#Beaufort Sea State during monitoring
#B1 
effort_B1 <- filter(effort_westerly, BEAUF == 1)
effort_B1_day <- hms(effort_B1$VIS_DAY_OBS) %>% period_to_seconds()
effort_B1_day <- (((sum(effort_B1_day, na.rm=TRUE))/60)/60)
effort_B1_night <- hms(effort_B1$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B1_night <- (((sum(effort_B1_night, na.rm=TRUE))/60)/60)
effort_B1_PAM <- hms(effort_B1$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B1_PAM <- (((sum(effort_B1_PAM, na.rm=TRUE))/60)/60)
effort_B1_P <- hms(effort_B1$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_B1_P <- (((sum(effort_B1_P, na.rm=TRUE))/60)/60)
b1 <- (effort_B1_day + effort_B1_night + effort_B1_PAM + effort_B1_P)
#B2
effort_B2 <- filter(effort_westerly, BEAUF == 2)
effort_B2_day <- hms(effort_B2$VIS_DAY_OBS) %>% period_to_seconds()
effort_B2_day <- (((sum(effort_B2_day, na.rm=TRUE))/60)/60)
effort_B2_night <- hms(effort_B2$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B2_night <- (((sum(effort_B2_night, na.rm=TRUE))/60)/60)
effort_B2_PAM <- hms(effort_B2$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B2_PAM <- (((sum(effort_B2_PAM, na.rm=TRUE))/60)/60)
effort_B2_P <- hms(effort_B2$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_B2_P <- (((sum(effort_B2_P, na.rm=TRUE))/60)/60)
b2 <- (effort_B2_day + effort_B2_night + effort_B2_PAM +effort_B2_P)
#B3
effort_B3 <- filter(effort_westerly, BEAUF == 3)
effort_B3_day <- hms(effort_B3$VIS_DAY_OBS) %>% period_to_seconds()
effort_B3_day <- (((sum(effort_B3_day, na.rm=TRUE))/60)/60)
effort_B3_night <- hms(effort_B3$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B3_night <- (((sum(effort_B3_night, na.rm=TRUE))/60)/60)
effort_B3_PAM <- hms(effort_B3$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B3_PAM <- (((sum(effort_B3_PAM, na.rm=TRUE))/60)/60)
effort_B3_PAM_d <- hms(effort_B3$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_B3_PAM_d <- (((sum(effort_B3_PAM_d, na.rm=TRUE))/60)/60)
b3<-(effort_B3_day + effort_B3_night + effort_B3_PAM+effort_B3_PAM_d)
#B4
effort_B4 <- filter(effort_westerly, BEAUF == 4)
effort_B4_day <- hms(effort_B4$VIS_DAY_OBS) %>% period_to_seconds()
effort_B4_day <- (((sum(effort_B4_day, na.rm=TRUE))/60)/60)
effort_B4_night <- hms(effort_B4$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B4_night <- (((sum(effort_B4_night, na.rm=TRUE))/60)/60)
effort_B4_PAM <- hms(effort_B4$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B4_PAM <- (((sum(effort_B4_PAM, na.rm=TRUE))/60)/60)
b4<-(effort_B4_day + effort_B4_night + effort_B4_PAM)

total <- b1+ b2+b3+b4
Beaufort = c("B1", "B2", "B3", "B4", "Total")
Duration <- c(b1, b2, b3, b4, total)%>% round(digits=2)
df<- data.frame(Beaufort=Beaufort, Duration=Duration)
  
Beauf_table <- gt(df) %>% cols_label(Beaufort = "Beaufort Sea State", Duration= "Duration (HH.HH)")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
Beauf_table
```

### Visual Detections

Total number of detection events by species:

```{r}
#| echo: false
#| warning: false

visualdetect_westerly <- visualdetect %>% filter(VESSEL == "Westerly")

#detections by species
species_summary <- visualdetect_westerly %>%
  count(NAME_COMMON)
species_table <- gt(species_summary) %>% cols_label(NAME_COMMON = "Species",
                                          n = "Number of detection records")%>% tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
species_table
```

Total detected individuals by species:

```{r}
#| echo: false
#| warning: false
visualdetect_westerly$RANGE_VESSEL_START <- as.numeric(visualdetect_westerly$RANGE_VESSEL_START)

individuals_summary <- visualdetect_westerly %>%
  group_by(NAME_COMMON) %>%
  summarize(
    total_value = sum(TOT_NUM),
            average_value = round(mean(TOT_NUM),1),
            dist_value = round(mean(RANGE_VESSEL_START),0))

ind_table <- gt(individuals_summary) %>% cols_label(NAME_COMMON = "Species",
                  total_value = "Individuals Count",
                  average_value = "Average group size",
                  dist_value = "Average distance (m) from vessel at first detection")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )

ind_table
```

Closest point of approach (CPA) to source (sparker) during detections:

```{r}
#| echo: false
#| warning: false
visualdetect_westerly$MITZONE_SILENTSOURCE_DIST <- as.numeric(visualdetect_westerly$MITZONE_SILENTSOURCE_DIST)
CPA <- visualdetect_westerly %>%
  group_by(NAME_COMMON) %>%
  summarize(active_value = round(mean(MITZONE_ACTIVESOURCE_DIST, na.rm = TRUE),2),
            inactive_value = round(mean(MITZONE_SILENTSOURCE_DIST, na.rm = TRUE),2))


CPA_table <- gt(CPA) %>% cols_label(NAME_COMMON = "Species",
                  active_value = "Mean CPA to active sparker (meters)",
                  inactive_value = "Mean CPA to silent sparker (meters)") %>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )

CPA_table
```

### Incidental Harassment Authorization (IHA) Level B Exposures

There were no IHA Level B exposures during the survey.

### Port Calls

Port calls during the survey:

```{r}
#| echo: false
#| warning: false

portcall_westerly <- portcall %>% filter(VESSEL == "Westerly")


portcall_table <- gt(portcall_westerly)%>% cols_label(PROJECT_NUMBER = "Project Number", VESSEL = "Vessel", DATE = "Date", TIME = "Time", PORT = "Port", ACTION = "Action", COMMENT_PORT_CALL= "Comments") %>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )

portcall_table
```

## Project 222072 (*Sanco Swift*)

### Operation Activity

Total hours of sparker operation:

```{r}
#| echo: false
#| warning: false

#load libraries
library(readr)
library(tidyverse)
library(dplyr)
library(tidyr)
library(stringr)
library(gt)

#import tidy data
#import with latin encoding because some PSO names have accents
visualdetect <- readr::read_csv("data/2023/COSW/COSW_VisualDetect_Tidy.csv", locale = locale(encoding = "latin1"))
effort <- readr::read_csv("data/2023/COSW/COSW_Effort_Tidy.csv", locale = locale(encoding = "latin1"))
operations <- readr::read_csv("data/2023/COSW/COSW_Operations_Tidy.csv", locale = locale(encoding = "latin1"))
portcall <- readr::read_csv("data/2023/COSW/COSW_PortCall_Tidy.csv", locale = locale(encoding = "latin1"))
operations_sanco <- operations %>% filter(VESSEL == "Sanco Swift") 

sparker_sursource <- operations_sanco %>% hms(operations_sanco$DUR_SURSOURCE) %>% period_to_seconds()
sparker_sursource <- (((sum(sparker_sursource, na.rm=TRUE))/60)/60)

sparker_soft <- operations_sanco %>% hms(operations_sanco$DUR_SOFTSTART) %>% period_to_seconds()
sparker_soft <- (((sum(sparker_soft, na.rm=TRUE))/60)/60)

sparker_test <- operations_sanco %>% hms(operations_sanco$DUR_TEST) %>% period_to_seconds()
sparker_test <- (((sum(sparker_test, na.rm=TRUE))/60)/60)

sparker_presursource <- operations_sanco %>% hms(operations_sanco$DUR_PRESURSOURCE) %>% period_to_seconds()
sparker_presursource <- (((sum(sparker_presursource, na.rm=TRUE))/60)/60)

sparker_postsur <- operations_sanco %>% hms(operations_sanco$DUR_POSTSUR) %>% period_to_seconds()
sparker_postsur <- (((sum(sparker_postsur, na.rm=TRUE))/60)/60)

sparker_reduce <- operations_sanco %>% hms(operations_sanco$DUR_REDUCEDOUTPUT) %>% period_to_seconds()
sparker_reduce <- (((sum(sparker_reduce, na.rm=TRUE))/60)/60)


total_sparkerop <- sum(sparker_sursource, sparker_soft, sparker_test, sparker_presursource, sparker_postsur, sparker_reduce)

vessel <- c("Sanco Swift")
date <- c("9/20/2023 - 5/31/2024")
operation <- c(total_sparkerop)%>% round(digits=2)
df <- data.frame(vessel = vessel, date=date, operation = operation)

op_table <- gt(df) %>% cols_label(vessel = "Survey Vessel", date= "Dates of Operation", operation= "Total Hours of Source Operation (HH.HH)")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
op_table
```

### Monitoring Effort

Summary of monitoring effort for survey:

```{r}
#| echo: false
#| warning: false
effort_sanco<- effort %>% filter(VESSEL == "Sanco Swift") 
day_obs <- hms(effort_sanco$VIS_DAY_OBS)
night_obs <- hms(effort_sanco$VIS_NIGHT_OBS)
#no acoustic observations
day_obs_sec <- period_to_seconds(day_obs)
day_obs_hrs <- (((sum(day_obs_sec, na.rm=TRUE))/60)/60)
night_obs_sec <- period_to_seconds(night_obs)
night_obs_hrs <- (((sum(night_obs_sec, na.rm=TRUE))/60)/60)

total_obs <- (day_obs_hrs + night_obs_hrs)
#sparkers active 

sparkers_day <- (hms(effort_sanco$SOURCE_DAY_OBS))
sparkers_day_sec <- period_to_seconds(sparkers_day)
sparkers_day_hrs <- (((sum(sparkers_day_sec, na.rm=TRUE))/60)/60)
sparkers_nite <- hms(effort_sanco$SOURCE_NIGHT_OBS)
sparkers_nite_sec <- period_to_seconds(sparkers_nite)
sparkers_nite_hrs <- (((sum(sparkers_nite_sec, na.rm=TRUE))/60)/60)

sparkers_active <- sum(sparkers_nite_hrs + sparkers_day_hrs)
sparkers_inactive <- total_obs -sparkers_active 

monitoring <- c("Sparker active", "Sparker not active", "Daytime", "Nighttime", "Total")
visual <- c(sparkers_active, sparkers_inactive, day_obs_hrs, night_obs_hrs,  total_obs) %>% round(digits=2)


df <- data.frame(Monitoring=monitoring, Visual = visual)

monitoring_table <- gt(df) %>% cols_label(Monitoring = "Monitoring effort", Visual= "Visual (HH.HH)")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
monitoring_table
```

### Environmental Conditions

Summary of visibility conditions during the survey:

```{r}
#| echo: false
#| warning: false

effort_sanco$VISIBIL <- gsub("5-Feb", "2-5", effort_sanco$VISIBIL)
effort_sanco$VISIBIL <- gsub("2-Jan", "1-2", effort_sanco$VISIBIL)
#visibility conditions
#print(unique(effort_westerly$VISIBIL))
#monitoring effort with >5 km visibiilIty = 2211.18 hrs
effort_highvis <- filter(effort_sanco, VISIBIL == ">5")
effort_high <- hms(effort_highvis$VIS_DAY_OBS) %>% period_to_seconds()
effort_high <- (((sum(effort_high, na.rm=TRUE))/60)/60)
effort_high_PV <- hms(effort_highvis$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_high_PV <- (((sum(effort_high_PV, na.rm=TRUE))/60)/60)
effort_night <- hms(effort_highvis$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_night <- (((sum(effort_night, na.rm=TRUE))/60)/60)
effort_high_P <- hms(effort_highvis$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_high_P <- (((sum(effort_high_P, na.rm=TRUE))/60)/60)
greater_five <- (effort_high + effort_high_PV + effort_night + effort_high_P)

effort_midvis <- filter(effort_sanco, VISIBIL == "2-5")
effort_midvis_day <- hms(effort_midvis$VIS_DAY_OBS) %>% period_to_seconds()
effort_midvis_day <- (((sum(effort_midvis_day, na.rm=TRUE))/60)/60)
effort_midvis_night <- hms(effort_midvis$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_midvis_night <- (((sum(effort_midvis_night, na.rm=TRUE))/60)/60)
effort_midvis_PV <- hms(effort_midvis$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_midvis_PV <- (((sum(effort_midvis_PV, na.rm=TRUE))/60)/60)
effort_midvis_P <- hms(effort_midvis$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_midvis_P <- (((sum(effort_midvis_P, na.rm=TRUE))/60)/60)

two_to_five <- (effort_midvis_day + effort_midvis_night + effort_midvis_P + effort_midvis_PV)

effort_lowvis <- filter(effort_sanco, VISIBIL == "0.5-1" | VISIBIL == "1-2" | VISIBIL == "0.05-0.1" |
                          VISIBIL == "0.3-0.5" | VISIBIL == "<.05" |VISIBIL == "0.1-0.3" )
effort_lowvis_day <- hms(effort_lowvis$VIS_DAY_OBS) %>% period_to_seconds()
effort_lowvis_day <- (((sum(effort_lowvis_day, na.rm=TRUE))/60)/60)
effort_lowvis_night <- hms(effort_lowvis$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_lowvis_night <- (((sum(effort_lowvis_night, na.rm=TRUE))/60)/60)
effort_lowvis_PV <- hms(effort_lowvis$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_lowvis_PV <- (((sum(effort_lowvis_PV, na.rm=TRUE))/60)/60)
effort_lowvis_P <- hms(effort_lowvis$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_lowvis_P <- (((sum(effort_lowvis_P, na.rm=TRUE))/60)/60)

less_than_2 <- (effort_lowvis_P + effort_lowvis_PV + effort_lowvis_night + effort_lowvis_day)

Visibility <- c("Greater than 5 km", "2 to 5 km", "Less than 2 km")
Duration <- c(greater_five, two_to_five, less_than_2) %>% round(digits=2)
df<- data.frame(Visibility=Visibility, Duration=Duration)
  
visibility_table <- gt(df) %>% cols_label(Visibility = "Visibility", Duration= "Duration (HH.HH)")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
visibility_table
```

Summary of swell height during the survey:

```{r}
#| echo: false
#| warning: false

effort_sanco$SWELL <- gsub("4-Feb", "2-4", effort_sanco$SWELL)
lowswell <- filter(effort_sanco, SWELL == "<2")
s_day <- hms(lowswell$VIS_DAY_OBS) %>% period_to_seconds()
s_day <- (((sum(s_day, na.rm=TRUE))/60)/60)
s_night <- hms(lowswell$VIS_NIGHT_OBS) %>% period_to_seconds()
s_night <- (((sum(s_night, na.rm=TRUE))/60)/60)
s_PAM <- hms(lowswell$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
s_PAM <- (((sum(s_PAM, na.rm=TRUE))/60)/60)
d_PAM <- hms(lowswell$VIS_PAM_DAY_OBS) %>% period_to_seconds()
d_PAM <- (((sum(d_PAM, na.rm=TRUE))/60)/60)
low_swell <- (s_day + s_night + s_PAM + d_PAM)
#swell 2-4 meters- 143.08 hrs
midswell <- filter(effort_sanco, SWELL == "2-4")
m_day <- hms(midswell$VIS_DAY_OBS) %>% period_to_seconds()
m_day <- (((sum(m_day, na.rm=TRUE))/60)/60)
m_night <- hms(midswell$VIS_NIGHT_OBS) %>% period_to_seconds()
m_night <- (((sum(m_night, na.rm=TRUE))/60)/60)
m_PAM <- hms(midswell$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
m_PAM <- (((sum(m_PAM, na.rm=TRUE))/60)/60)
mid_swell <- (m_day + m_night + m_PAM)
#swell 2-4 meters- 143.08 hrs
highswell <- filter(effort_sanco, SWELL == ">4")
h_day <- hms(highswell$VIS_DAY_OBS) %>% period_to_seconds()
h_day <- (((sum(h_day, na.rm=TRUE))/60)/60)
h_night <- hms(highswell$VIS_NIGHT_OBS) %>% period_to_seconds()
h_night <- (((sum(h_night, na.rm=TRUE))/60)/60)
h_PAM <- hms(highswell$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
h_PAM <- (((sum(h_PAM, na.rm=TRUE))/60)/60)
high_swell <- (h_day + h_night + h_PAM)

Swell = c("Less than 2 m", "2 to 4 m", "Greater than 4 m")
Duration <- c(low_swell, mid_swell, high_swell)%>% round(digits=2)
df<- data.frame(Swell=Swell, Duration=Duration)
  
Swell_table <- gt(df) %>% cols_label(Swell = "Swell", Duration= "Duration (HH.HH)")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
Swell_table
```

Summary of Beaufort Sea State during the survey:

```{r}
#| echo: false
#| warning: false

#Beaufort Sea State during monitoring
#B1 
effort_B1 <- filter(effort_sanco, BEAUF == 1)
effort_B1_day <- hms(effort_B1$VIS_DAY_OBS) %>% period_to_seconds()
effort_B1_day <- (((sum(effort_B1_day, na.rm=TRUE))/60)/60)
effort_B1_night <- hms(effort_B1$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B1_night <- (((sum(effort_B1_night, na.rm=TRUE))/60)/60)
effort_B1_PAM <- hms(effort_B1$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B1_PAM <- (((sum(effort_B1_PAM, na.rm=TRUE))/60)/60)
effort_B1_P <- hms(effort_B1$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_B1_P <- (((sum(effort_B1_P, na.rm=TRUE))/60)/60)
b1 <- (effort_B1_day + effort_B1_night + effort_B1_PAM + effort_B1_P)
#B2
effort_B2 <- filter(effort_sanco, BEAUF == 2)
effort_B2_day <- hms(effort_B2$VIS_DAY_OBS) %>% period_to_seconds()
effort_B2_day <- (((sum(effort_B2_day, na.rm=TRUE))/60)/60)
effort_B2_night <- hms(effort_B2$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B2_night <- (((sum(effort_B2_night, na.rm=TRUE))/60)/60)
effort_B2_PAM <- hms(effort_B2$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B2_PAM <- (((sum(effort_B2_PAM, na.rm=TRUE))/60)/60)
effort_B2_P <- hms(effort_B2$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_B2_P <- (((sum(effort_B2_P, na.rm=TRUE))/60)/60)
b2 <- (effort_B2_day + effort_B2_night + effort_B2_PAM +effort_B2_P)
#B3
effort_B3 <- filter(effort_sanco, BEAUF == 3)
effort_B3_day <- hms(effort_B3$VIS_DAY_OBS) %>% period_to_seconds()
effort_B3_day <- (((sum(effort_B3_day, na.rm=TRUE))/60)/60)
effort_B3_night <- hms(effort_B3$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B3_night <- (((sum(effort_B3_night, na.rm=TRUE))/60)/60)
effort_B3_PAM <- hms(effort_B3$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B3_PAM <- (((sum(effort_B3_PAM, na.rm=TRUE))/60)/60)
effort_B3_PAM_d <- hms(effort_B3$VIS_PAM_DAY_OBS) %>% period_to_seconds()
effort_B3_PAM_d <- (((sum(effort_B3_PAM_d, na.rm=TRUE))/60)/60)
b3<-(effort_B3_day + effort_B3_night + effort_B3_PAM+effort_B3_PAM_d)
#B4
effort_B4 <- filter(effort_sanco, BEAUF == 4)
effort_B4_day <- hms(effort_B4$VIS_DAY_OBS) %>% period_to_seconds()
effort_B4_day <- (((sum(effort_B4_day, na.rm=TRUE))/60)/60)
effort_B4_night <- hms(effort_B4$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B4_night <- (((sum(effort_B4_night, na.rm=TRUE))/60)/60)
effort_B4_PAM <- hms(effort_B4$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B4_PAM <- (((sum(effort_B4_PAM, na.rm=TRUE))/60)/60)
b4<-(effort_B4_day + effort_B4_night + effort_B4_PAM)
#B5
effort_B5 <- filter(effort_sanco, BEAUF == 5)
effort_B5_day <- hms(effort_B5$VIS_DAY_OBS) %>% period_to_seconds()
effort_B5_day <- (((sum(effort_B5_day, na.rm=TRUE))/60)/60)
effort_B5_night <- hms(effort_B5$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B5_night <- (((sum(effort_B5_night, na.rm=TRUE))/60)/60)
effort_B5_PAM <- hms(effort_B5$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B5_PAM <- (((sum(effort_B5_PAM, na.rm=TRUE))/60)/60)
b5<-(effort_B5_day + effort_B5_night + effort_B5_PAM)
#B6
effort_B6 <- filter(effort_sanco, BEAUF == 6)
effort_B6_day <- hms(effort_B6$VIS_DAY_OBS) %>% period_to_seconds()
effort_B6_day <- (((sum(effort_B6_day, na.rm=TRUE))/60)/60)
effort_B6_night <- hms(effort_B6$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B6_night <- (((sum(effort_B6_night, na.rm=TRUE))/60)/60)
effort_B6_PAM <- hms(effort_B6$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B6_PAM <- (((sum(effort_B6_PAM, na.rm=TRUE))/60)/60)
b6<-(effort_B6_day + effort_B6_night + effort_B6_PAM)
#B7
effort_B7 <- filter(effort_sanco, BEAUF == 7)
effort_B7_day <- hms(effort_B7$VIS_DAY_OBS) %>% period_to_seconds()
effort_B7_day <- (((sum(effort_B7_day, na.rm=TRUE))/60)/60)
effort_B7_night <- hms(effort_B7$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B7_night <- (((sum(effort_B7_night, na.rm=TRUE))/60)/60)
effort_B7_PAM <- hms(effort_B7$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B7_PAM <- (((sum(effort_B7_PAM, na.rm=TRUE))/60)/60)
b7<-(effort_B7_day + effort_B7_night + effort_B7_PAM)
#B8
effort_B8 <- filter(effort_sanco, BEAUF == 8)
effort_B8_day <- hms(effort_B8$VIS_DAY_OBS) %>% period_to_seconds()
effort_B8_day <- (((sum(effort_B8_day, na.rm=TRUE))/60)/60)
effort_B8_night <- hms(effort_B8$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B8_night <- (((sum(effort_B8_night, na.rm=TRUE))/60)/60)
effort_B8_PAM <- hms(effort_B8$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B8_PAM <- (((sum(effort_B8_PAM, na.rm=TRUE))/60)/60)
b8<-(effort_B8_day + effort_B8_night + effort_B8_PAM)
#B9
effort_B9 <- filter(effort_sanco, BEAUF == 9)
effort_B9_day <- hms(effort_B9$VIS_DAY_OBS) %>% period_to_seconds()
effort_B9_day <- (((sum(effort_B9_day, na.rm=TRUE))/60)/60)
effort_B9_night <- hms(effort_B9$VIS_NIGHT_OBS) %>% period_to_seconds()
effort_B9_night <- (((sum(effort_B9_night, na.rm=TRUE))/60)/60)
effort_B9_PAM <- hms(effort_B9$VIS_PAM_NIGHT_OBS) %>% period_to_seconds()
effort_B9_PAM <- (((sum(effort_B9_PAM, na.rm=TRUE))/60)/60)
b9<-(effort_B9_day + effort_B9_night + effort_B9_PAM)

total <- b1+ b2+b3+b4+b5+b6+b7+b8+b9
Beaufort = c("B1", "B2", "B3", "B4","B5", "B6", "B7", "B8", "B9" ,"Total")
Duration <- c(b1, b2, b3, b4,b5, b6, b7, b8, b9, total)%>% round(digits=2)
df<- data.frame(Beaufort=Beaufort, Duration=Duration)
  
Beauf_table <- gt(df) %>% cols_label(Beaufort = "Beaufort Sea State", Duration= "Duration (HH.HH)")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
Beauf_table
```

### Visual Detections

Total number of detection events by species:

```{r}
#| echo: false
#| warning: false

visualdetect_sanco <- visualdetect %>% filter(VESSEL == "Sanco Swift")

#detections by species
species_summary <- visualdetect_sanco %>%
  count(NAME_COMMON)
species_table <- gt(species_summary) %>% cols_label(NAME_COMMON = "Species",
                                          n = "Number of detection records")%>% tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )
species_table
```

Total detected individuals by species:

\[AVG DISTANCE AT FIRST DETECTION IS DIFFERENT FROM WHAT IS REPORTED FOR HUMPBACK WHALE\]

```{r}
#| echo: false
#| warning: false
visualdetect_sanco$NAME_COMMON <- gsub("Unidentifiable Baleen whale", "Unidentifiable whale", visualdetect_sanco$NAME_COMMON)

visualdetect_sanco$RANGE_VESSEL_START <- as.numeric(visualdetect_sanco$RANGE_VESSEL_START)

individuals_summary <- visualdetect_sanco %>%
  group_by(NAME_COMMON) %>%
  summarize(
    total_value = sum(TOT_NUM),
            average_value = round(mean(TOT_NUM),1),
            dist_value = round(mean(RANGE_VESSEL_START),0))

ind_table <- gt(individuals_summary) %>% cols_label(NAME_COMMON = "Species",
                  total_value = "Individuals Count",
                  average_value = "Average group size",
                  dist_value = "Average distance (m) at first detection")%>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )

ind_table
```

Closest point of approach (CPA) to source (sparker) during the survey:

\[MEAN CPA TO ACTIVE SPARKER FOR HARBOR SEAL DIFFERENT FROM WHAT IS REPORTED\]

```{r}
#| echo: false
#| warning: false
visualdetect_sanco$MITZONE_SILENTSOURCE_DIST <- as.numeric(visualdetect_sanco$MITZONE_SILENTSOURCE_DIST)
CPA <- visualdetect_sanco %>%
  group_by(NAME_COMMON) %>%
  summarize(active_value = round(mean(MITZONE_ACTIVESOURCE_DIST, na.rm = TRUE),2),
            inactive_value = round(mean(MITZONE_SILENTSOURCE_DIST, na.rm = TRUE),2))


CPA_table <- gt(CPA) %>% cols_label(NAME_COMMON = "Species",
                  active_value = "Mean CPA to active sparker (meters)",
                  inactive_value = "Mean CPA to silent sparker (meters)") %>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )

CPA_table
```

### Incidental Harassment Authorization (IHA) Level B Exposures

```{r}
#| echo: false 
#| warning: false  
 
take <- visualdetect_sanco %>% group_by(NAME_COMMON) %>%   
  summarize(take_value = sum(LEVELB_TAKE, na.rm = TRUE))   

take_table <- gt(take) %>% cols_label(NAME_COMMON = "Species", take_value = "Total Number of Animals Observed Inside the Level B Harassment Zone") %>%  tab_options(     data_row.padding = px(1),     table.align = "left"   )  

take_table
```

### Port Calls

Port calls during the survey:

```{r}
#| echo: false
#| warning: false

portcall_sanco <- portcall %>% filter(VESSEL == "Sanco Swift")

portcall_table <- gt(portcall_sanco)%>% cols_label(PROJECT_NUMBER = "Project Number", VESSEL = "Vessel", DATE = "Date", TIME = "Time", PORT = "Port", ACTION = "Action", COMMENT_PORT_CALL= "Comments") %>%  tab_options(
    data_row.padding = px(1),
    table.align = "left"
  )

portcall_table
```
